---
title: "Fitting curves"
author: "Presley Kimball"
date: "2024-05-24"
output: html_document
--- 

## Initialize packages and data
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
require("haven")
require("doBy")
library(ggplot2)
library(dplyr)
library(RColorBrewer)
library("viridis") 
library(tigris)
library(tmap)
library(sf) 
library(dotwhisker)
library(gapminder)
library(maps)
library(broom)
library(gridExtra)
library("gridBase")
library("gridGraphics")
library(cowplot)
library(stargazer)
```


```{r}
palette_4 <- brewer.pal(4, "Spectral") 
palette_5 <- brewer.pal(5, "Spectral") 
gradient_palette <- "Spectral"
```

## Load in clean data
```{r}
setwd("FILLIN")
# these files are protected and cannot be posted to git hub. Put data folder
# in exterior folder to repository.
load("data/hosp_data_clean.RData")
load("data/param_dat_sum.RData")
```


## Age Analysis
```{r}
counts_by_age <- dat_sum %>%
  group_by(age_midpoint) %>%
  summarise(total_count = sum(rsv.sum))

age_counts <- counts_by_age %>% 
  ggplot(aes(x=age_midpoint, y=total_count)) + 
  geom_bar(stat = "identity")+
  labs(x = "Age Midpoint", y = "Count")

under20_age_counts <- counts_by_age[counts_by_age$age_midpoint<20,] %>% 
  ggplot(aes(x=age_midpoint, y=total_count)) + 
  geom_bar(stat = "identity")+
  labs(x = "Age Midpoint", y = "Count")


# attach pop density and urban_cat s to dat_sum
dat_sum$pop_density <- numeric(nrow(dat_sum))
dat_sum$population <- numeric(nrow(dat_sum))
dat_sum$urban_cat <- numeric(nrow(dat_sum))
dat_sum$urban_rural <- numeric(nrow(dat_sum))
for (i in 1:nrow(dat_sum)) {
  dat_sum$pop_density[i] <-
    hosp_data_clean$pop_density[hosp_data_clean$Hosptco==dat_sum$HOSPSTCO[i]]
  dat_sum$urban_cat[i] <-
    hosp_data_clean$urban_cat[hosp_data_clean$Hosptco==dat_sum$HOSPSTCO[i]]
  dat_sum$urban_rural[i] <-
    hosp_data_clean$urban_rural[hosp_data_clean$Hosptco==dat_sum$HOSPSTCO[i]]
  dat_sum$population[i] <-
    hosp_data_clean$population[hosp_data_clean$Hosptco==dat_sum$HOSPSTCO[i]]
}
```


## Subset under 10 and under 20
Take just the ages under 20,10 for fitting. This stops overfitting of older ages (since all around 0).

Create subset for under20 and under10 and then plot again
```{r}
# create subset of only younger age groups.
dat_sum_under20 <- dat_sum[dat_sum$age_midpoint<20,]
dat_sum_under10 <- dat_sum[dat_sum$age_midpoint<10,]

#plot this subset
for(i in 1:5){
  # create subset of current hospital
  sub <- dat_sum_under20[dat_sum_under20$HOSPSTCO==hosp_data_clean$Hosptco[i],]
    # plot the proportions
    plot(sub$age_midpoint, sub$rsv_proportion, main = hosp_data_clean$Hosptco[i],
         col = ifelse(sub$rsv_proportion == 0, "red", "blue"),pch = 19)
}
```


## Find non-conforming data (OK)
There exists some data which the second age group has a higher RSV proportion than the first. Let us investigate this data.
```{r}
subset_0.5 <- dat_sum_under20[dat_sum_under20$age_midpoint==0.5,]
subset_1.5 <- dat_sum_under20[dat_sum_under20$age_midpoint==1.5,]

hosp_data_clean$rsv_0.5 <- numeric(nrow(hosp_data_clean))
hosp_data_clean$rsv_1.5 <- numeric(nrow(hosp_data_clean))

for (i in 1:nrow(hosp_data_clean)){
  hosp_data_clean$rsv_0.5[i] <- subset_0.5$rsv_proportion[subset_0.5$HOSPSTCO==hosp_data_clean$Hosptco[i]]
  hosp_data_clean$rsv_1.5[i] <- subset_1.5$rsv_proportion[subset_1.5$HOSPSTCO==hosp_data_clean$Hosptco[i]]
}

bad_hosp_data <- hosp_data_clean[hosp_data_clean$rsv_0.5<hosp_data_clean$rsv_1.5,]
hosp_data_clean <- subset(hosp_data_clean, select = - rsv_1.5)
hosp_data_clean <- subset(hosp_data_clean, select = - rsv_0.5)
print(bad_hosp_data$rsv.HOSPST)
```
We found that the non-conforming data all comes from OK. We will assume that this is mainly due to some reporting practice in that state and thus remove OK for all future analyses.
```{r}
hosp_data_nobump <- hosp_data_clean[!(hosp_data_clean$rsv.HOSPST == "OK"),] 
dat_sum_under20_nobump <- subset(dat_sum_under20, (HOSPSTCO %in% hosp_data_nobump$Hosptco))
dat_sum_under10_nobump <- subset(dat_sum_under10, (HOSPSTCO %in% hosp_data_nobump$Hosptco))
```

## Statistical tests for differneces in urban vs rural- RSV proportion
First we will do ANOVA tests
- Test if RSV proportion has statistically significant differences for each age group among urban categories
- Let $\mu^{\text{age}}_{\text{cat}}$ be the mean rsv proportion of a given age group and urban category
- We will test for significant differences for RSV_proportions under 10 and under 20 to determine which subset to use. We find that the differences are only gauranteed to be significant for those ages under 10, and thus will use the under 10 subset for the duration of this study.

$$H_0: \mu^{\text{age}}_{\text{Metro}}=\mu^{\text{age}}_{\text{Micro}}=\mu^{\text{age}}_{\text{Rural}}$$

$$H_1: \text{at least one mean is different.}$$
Run QQ-plots to make sure test assumptions are met.
```{r}
unique_ages = unique(dat_sum_under20_nobump$age_midpoint)

for (i in 1:length(unique_ages)) {
  current_age = unique_ages[i]
  sub_metro <- dat_sum_under20_nobump[dat_sum_under20_nobump$age_midpoint == current_age &
                                        dat_sum_under20_nobump$urban_cat =="Metro",]
  sub_micro <- dat_sum_under20_nobump[dat_sum_under20_nobump$age_midpoint == current_age &
                                        dat_sum_under20_nobump$urban_cat =="Micro",]
  sub_rural <- dat_sum_under20_nobump[dat_sum_under20_nobump$age_midpoint == current_age &
                                        dat_sum_under20_nobump$urban_cat =="Rural",]
  qqnorm(sub_metro$rsv_proportion, pch = 1, frame = FALSE,main = paste("Metro, age =",current_age))
  qqline(sub_metro$rsv_proportion, col = "steelblue", lwd = 2)
  qqnorm(sub_micro$rsv_proportion, pch = 1, frame = FALSE,main = paste("Micro, age =",current_age))
  qqline(sub_micro$rsv_proportion, col = "steelblue", lwd = 2)
  qqnorm(sub_rural$rsv_proportion, pch = 1, frame = FALSE,main = paste("Rural, age =",current_age))
  qqline(sub_rural$rsv_proportion, col = "steelblue", lwd = 2)
}

```
These qqplots are generally bad for ages higher than 3.5, and the metro category always looks poor. However, should be fine to run statistical tests.

General statistics:
```{r}
for (i in 1:length(unique_ages)) {
  current_age = unique_ages[i]
  sub <- dat_sum_under20_nobump[dat_sum_under20_nobump$age_midpoint == current_age,]
  summary_stat<-sub %>%
    group_by(urban_cat) %>%
    summarise(
      mean = mean(rsv_proportion),
      sd = sd(rsv_proportion)
      )
  colnames(summary_stat) <- c(current_age,"mean","sd")
  print(summary_stat)
}


```

Can see some difference in the means until older ages again. Thus, ANOVA test makes sense.

ANOVA for under 10.
```{r}
unique_ages = unique(dat_sum_under10_nobump$age_midpoint)
for (i in 1:length(unique_ages)) {
  current_age = unique_ages[i]
  sub <- dat_sum_under10_nobump[dat_sum_under10_nobump$age_midpoint == current_age,]
  Anova_result <- aov(rsv_proportion ~ urban_cat, data = sub)
  print(current_age)
  print(summary(Anova_result))
  print(TukeyHSD(Anova_result))
}
```

> We see somethings similar here. Under 4.5, all groups are statistically significant. At 4.5, none are different. However, after 4.5 we see that both metro and micro are statistically significant from rural. That is interesting since it may indicate that there are strong distinctions between rural and other groups majority of the time.


## Functions for fitting by non-linear least squares (nls) for age_midpoint
List of functions
```{r}
tabl <- "
| name   | function |
|--------|----------|
| model1 | a e^{-bx} |
| model2 | k/(x^2)  |
| model3 | a x^{-b} |
| model4 | k e^{-kx}|
"
cat(tabl) # output
```

Functions for fitting
```{r}
model1_fit <- function(hospital_df,data_df,taga,tagb,tagerror,tagMSE){
  hospital_df[[taga]] <- numeric(nrow(hospital_df))
  hospital_df[[tagb]] <- numeric(nrow(hospital_df))
  hospital_df[[tagerror]] <- numeric(nrow(hospital_df))
  hospital_df[[tagMSE]] <- numeric(nrow(hospital_df))
  for (i in 1:nrow(hospital_df)){
    sub <- data_df[data_df$HOSPSTCO==hospital_df$Hosptco[i],] 
    x <- sub$age_midpoint
    y <- sub$rsv_proportion
    
    # fit to y = a*e^(-bx) 
    start_values <- c(a=1, b=1)
    fit <- nls(y ~ a * exp(-b * x),
           start = start_values,
           algorithm = "port",
           control = nls.control(maxiter = 1000))
    fit_coef <- coef(fit)
    hospital_df[[taga]][i] <- fit_coef["a"]
    hospital_df[[tagb]][i] <- fit_coef["b"]
    hospital_df[[tagerror]][i] <- sum(residuals(fit)^2)
    hospital_df[[tagMSE]][i] <- mean(residuals(fit)^2)
  }
  return(hospital_df)
}



model2_fit <- function(hospital_df,data_df,tagk,tagerror,tagMSE){
  hospital_df[[tagk]] <- numeric(nrow(hospital_df))
  hospital_df[[tagerror]] <- numeric(nrow(hospital_df))
  hospital_df[[tagMSE]] <- numeric(nrow(hospital_df))
  for (i in 1:nrow(hospital_df)){
    sub <- data_df[data_df$HOSPSTCO==hospital_df$Hosptco[i],] 
    x <- sub$age_midpoint
    y <- sub$rsv_proportion
    
    # fit to y = k/x^2
    start_values <- c(k=1)
    fit <- nls(y ~ k/(x^2),
           start = start_values,
           algorithm = "port",
           control = nls.control(maxiter = 1000))
    fit_coef <- coef(fit)
    hospital_df[[tagk]][i] <- fit_coef["k"]
    hospital_df[[tagerror]][i] <- sum(residuals(fit)^2)
    hospital_df[[tagMSE]][i] <- mean(residuals(fit)^2)
  }
  return(hospital_df)
}

model3_fit <- function(hospital_df,data_df,taga,tagb,tagerror,tagMSE){
  hospital_df[[taga]] <- numeric(nrow(hospital_df))
  hospital_df[[tagb]] <- numeric(nrow(hospital_df))
  hospital_df[[tagerror]] <- numeric(nrow(hospital_df))
  hospital_df[[tagMSE]] <- numeric(nrow(hospital_df))
  for (i in 1:nrow(hospital_df)){
    sub <- data_df[data_df$HOSPSTCO==hospital_df$Hosptco[i],] 
    x <- sub$age_midpoint
    y <- sub$rsv_proportion
    
    # fit to y = a*x^(-b) 
    start_values <- c(a=1, b=2)
    fit <- nls(y ~ a*x^(-b),
           start = start_values,
           algorithm = "port",
           control = nls.control(maxiter = 1000))
    fit_coef <- coef(fit)
    hospital_df[[taga]][i] <- fit_coef["a"]
    hospital_df[[tagb]][i] <- fit_coef["b"]
    hospital_df[[tagerror]][i] <- sum(residuals(fit)^2)
    hospital_df[[tagMSE]][i] <- mean(residuals(fit)^2)
  }
  return(hospital_df)
}

model4_fit <- function(hospital_df,data_df,tagk,tagerror,tagMSE){
  hospital_df[[tagk]] <- numeric(nrow(hospital_df))
  hospital_df[[tagerror]] <- numeric(nrow(hospital_df))
  hospital_df[[tagMSE]] <- numeric(nrow(hospital_df))
  for (i in 1:nrow(hospital_df)){
    sub <- data_df[data_df$HOSPSTCO==hospital_df$Hosptco[i],] 
    x <- sub$age_midpoint
    y <- sub$rsv_proportion
    
    # fit to y = ke^(-kx)
    start_values <- c(k=1.5)
    fit <- nls(y ~ k*exp(-k*x),
           start = start_values,
           algorithm = "port",
           control = nls.control(maxiter = 5000))
    fit_coef <- coef(fit)
    hospital_df[[tagk]][i] <- fit_coef["k"]
    hospital_df[[tagerror]][i] <- sum(residuals(fit)^2)
    hospital_df[[tagMSE]][i] <- mean(residuals(fit)^2)
  }
  return(hospital_df)
}

```

Fitting to data using functions
```{r}
#fit on data under 10
hosp_data_nobump<-model1_fit(hosp_data_nobump,dat_sum_under10_nobump,"und10_model1_a",
                            "und10_model1_b","und10_model1_sumerror","und10_model1_MSE")
hosp_data_nobump<-model2_fit(hosp_data_nobump,dat_sum_under10_nobump,"und10_model2_k",
                            "und10_model2_sumerror","und10_model2_MSE")
hosp_data_nobump<-model3_fit(hosp_data_nobump,dat_sum_under10_nobump,"und10_model3_a",
                            "und10_model3_b","und10_model3_sumerror","und10_model3_MSE")
hosp_data_nobump<-model4_fit(hosp_data_nobump,dat_sum_under10_nobump,"und10_model4_k",
                            "und10_model4_sumerror","und10_model4_MSE")
hosp_data_nobump[hosp_data_nobump$und10_model4_k<4,]
```

## Plots of nls fits for under 10

Plot any fit
```{r}
# create domain for plot
ages <- seq(0, 10, length.out = 100) 

for (i in 1:10){
  current_code <- hosp_data_nobump$Hosptco[i]
  model1_predict <- hosp_data_nobump$und10_model1_a[i] * exp( -hosp_data_nobump$und10_model1_b[i] * ages)
  model2_predict <- hosp_data_nobump$und10_model2_k[i]/(ages^2)
  model3_predict <- hosp_data_nobump$und10_model3_a[i]*ages^(-hosp_data_nobump$und10_model3_b[i])
  model4_predict <- hosp_data_nobump$und10_model4_k[i] * exp(-hosp_data_nobump$und10_model4_k[i] * ages)
  sub <- dat_sum_under10[dat_sum_under10$HOSPSTCO == current_code,]

  plot(sub$age_midpoint,sub$rsv_proportion, main = current_code, col = 'black',
       pch =19,cex=1.5, xlab = "Age",ylab = "Proportion of Cases")
  lines(ages,model1_predict, col=palette_4[1],lwd =2)
  lines(ages,model2_predict, col=palette_4[2],lwd =2)
  lines(ages,model3_predict, col=palette_4[3],lwd =2)
  lines(ages,model4_predict, col=palette_4[4],lwd =2)
  points(sub$age_midpoint,sub$rsv_proportion,col = 'black',pch =19,cex=1.5)
  legend("topright",
         legend = c("data","ae^(-bx)","k/x^2","ax^(-b)","ke^(-kx))"),
         col=c('black',palette_4[1],
               palette_4[2],palette_4[3],palette_4[4]),lty = 1,lwd=c(2,2,2,2,2))
}
```

```{r}
ages <- seq(0, 10, length.out = 100) 
Counties <- c("New York", "Cook","Denver", "Philadelphia")

make_county_plot <- function(i){
current_county <- Counties[i]

  current_code <- hosp_data_nobump$Hosptco[hosp_data_nobump$county == current_county]
  model1_predict <- hosp_data_nobump$und10_model1_a[i] * exp( -hosp_data_nobump$und10_model1_b[i] * ages)
  model2_predict <- hosp_data_nobump$und10_model2_k[i]/(ages^2)
  model3_predict <- hosp_data_nobump$und10_model3_a[i]*ages^(-hosp_data_nobump$und10_model3_b[i])
  model4_predict <- hosp_data_nobump$und10_model4_k[i] * exp(-hosp_data_nobump$und10_model4_k[i] * ages)
  sub <- dat_sum_under10[dat_sum_under10$HOSPSTCO == current_code,]
  par(mar = c(3, 4.1, 2.1, 0.5),las = 1)
  plot(sub$age_midpoint,sub$rsv_proportion, 
       col = 'black',pch =19,cex=0.8, xlab = " ",ylab = "Prop. of Cases")
  title(main =paste(current_county,
                    hosp_data_nobump$rsv.HOSPST[hosp_data_nobump$Hosptco == 
                                                  current_code],sep = ", "),line = 0.6)
  mtext("Age", side = 1, line = 2)
  lines(ages,model1_predict, col=palette_4[1],lwd =2)
  lines(ages,model2_predict, col=palette_4[2],lwd =2)
  lines(ages,model3_predict, col=palette_4[3],lwd =2)
  lines(ages,model4_predict, col=palette_4[4],lwd =2)
  points(sub$age_midpoint,sub$rsv_proportion,col = 'black',pch =19,cex=1)
}

current_county <- Counties[3]

  current_code <- hosp_data_nobump$Hosptco[hosp_data_nobump$county == current_county]
  sub <- dat_sum_under10[dat_sum_under10$HOSPSTCO == current_code,]
  par(mar = c(3, 4.1, 2.1, 0.5),las = 1)
  plot(sub$age_midpoint,sub$rsv_proportion, 
       col = 'black',pch =19,cex=1.5, xlab = " ",ylab = "Prop. of Cases")
  title(main =paste(current_county,
                    hosp_data_nobump$rsv.HOSPST[hosp_data_nobump$Hosptco == 
                                                  current_code],sep = ", "),line = 0.6)
  mtext("Age", side = 1, line = 2)
  
NY_plot <- function(){
  make_county_plot(1)
}

IL_plot <- function(){
  make_county_plot(2)
}
CO_plot <- function(){
  make_county_plot(3)
}
PA_plot <- function(){
  make_county_plot(4)
}
make_legend <-function(){
  par(mar = c(1, 4.1, 2.1, 0.5))
plot(NULL ,xaxt='n',yaxt='n',bty='n',ylab='',xlab='', xlim=0:1, ylim=0:1)
legend("center",
         legend = c("actual","ae^(-bx)","k/x^2","ax^(-b)","ke^(-kx))"),
         col=c('black',palette_4[1],
               palette_4[2],palette_4[3],palette_4[4]),pch = c(19,NA,NA,NA,NA),lty = c(0,1,1,1,1),lwd=c(2,2,2,2,2))
}

ggdraw(NY_plot)
ggdraw(IL_plot)
ggdraw(CO_plot)
ggdraw(PA_plot)
ggdraw(make_legend)
margin_try <- c(3, 4.1, 2.1, 0.5)
plot_grid(NY_plot,make_legend,CO_plot,PA_plot,nrow = 2)
mult_loc <- plot_grid(NY_plot, make_legend, CO_plot, PA_plot, nrow = 2)
```



Plots of the worst and the best 
```{r}
# want a list of the top 5 and the bottom 5
loop_range = c(1:2,(nrow(hosp_data_nobump)-4):nrow(hosp_data_nobump))

hosp_data_nobump <- hosp_data_nobump[order(hosp_data_nobump$und10_model1_MSE,
                                           decreasing = FALSE),]

for (i in loop_range){
  current_code <- hosp_data_nobump$Hosptco[i]
  model1_predict <- hosp_data_nobump$und10_model1_a[i] * exp( -hosp_data_nobump$und10_model1_b[i] * ages)
  sub <- dat_sum_under10[dat_sum_under10$HOSPSTCO == current_code,]
  plot(sub$age_midpoint,sub$rsv_proportion, col = 'black', pch =19,  cex = 1.5,
       main=paste("#",i,":Hospital", current_code, "with MSE", hosp_data_nobump$und10_model1_MSE[i]),
       xlab = "Age", ylab = "Proportion of Cases")
  lines(ages,model1_predict, col=palette_4[1],lwd = 2)
  legend("topright",legend = c("actual","ae^(bx)"),col=c("black",palette_4[1]),lty = 1,,lwd = 2)
}

hosp_data_nobump <- hosp_data_nobump[order(hosp_data_nobump$und10_model2_MSE,
                                           decreasing = FALSE),]


for (i in loop_range){
  current_code <- hosp_data_nobump$Hosptco[i]
  model2_predict <- hosp_data_nobump$und10_model2_k[i]/(ages^2)
  sub <- dat_sum_under10[dat_sum_under10$HOSPSTCO == current_code,]

  plot(sub$age_midpoint,sub$rsv_proportion, col = 'black', pch =19,  cex = 1.5,
       main=paste("#",i,":Hospital", current_code, ", MSE", hosp_data_nobump$und10_model2_MSE[i]),
       xlab = "Age", ylab = "Proportion of Cases")
  lines(ages,model2_predict, col=palette_4[2],lwd = 2)
  legend("topright",legend = c("actual","k/x^2"),col=c("black",palette_4[2]),lty = 1,,lwd = 2)
}

hosp_data_nobump <- hosp_data_nobump[order(hosp_data_nobump$und10_model3_MSE,
                                           decreasing = FALSE),]

for (i in loop_range){
  current_code <- hosp_data_nobump$Hosptco[i]
  model3_predict <- hosp_data_nobump$und10_model3_a[i]*ages^(-hosp_data_nobump$und10_model3_b[i])
  sub <- dat_sum_under10[dat_sum_under10$HOSPSTCO == current_code,]

  plot(sub$age_midpoint,sub$rsv_proportion, col = 'black', pch =19,  cex = 1.5,
       main=paste("#",i,":Hospital", current_code, ", MSE", hosp_data_nobump$und10_model3_MSE[i]),
       xlab = "Age", ylab = "Proportion of Cases")
  lines(ages,model3_predict, col=palette_4[3],lwd = 2)
  legend("topright",legend = c("actual","ax^(-b)"),col=c("black",palette_4[3]),lty = 1,,lwd = 2)
}

hosp_data_nobump <- hosp_data_nobump[order(hosp_data_nobump$und10_model4_sumerror,
                                           decreasing = FALSE),]

for (i in loop_range){
  current_code <- hosp_data_nobump$Hosptco[i]
  model4_predict <- hosp_data_nobump$und10_model4_k[i] * exp(-hosp_data_nobump$und10_model4_k[i] * ages)
  sub <- dat_sum_under10[dat_sum_under10$HOSPSTCO == current_code,]
  plot(sub$age_midpoint,sub$rsv_proportion, col = 'black', pch =19,  cex = 1.5,
       main=paste("#",i,":Hospital", current_code, ", MSE", hosp_data_nobump$und10_model4_MSE[i]),
       xlab = "Age", ylab = "Proportion of Cases")
  lines(ages,model4_predict, col=palette_4[4],lwd = 2)
  legend("topright",legend = c("actual","ke^(-kx))"),col=c("black",palette_4[4]),lty = 1,,lwd = 2)
}

tail(hosp_data_nobump)
```

## Error statistics of nls fits

```{r}
subset <- hosp_data_nobump
Sum_Errors <- subset[,c("und10_model1_sumerror","und10_model2_sumerror",
                                  "und10_model3_sumerror","und10_model4_sumerror")]
colnames(Sum_Errors) <- c("y = a e^(-b x)","y = k/x^2","y =a x^(-b)","y =k e^(-kx)")
sum_error_means <- colMeans(Sum_Errors)
Sum_Errors <- Sum_Errors[order(sum_error_means)] 
sum_error_means <- sum_error_means[order(sum_error_means)]
print("Sum squared error means by group:")
print(sum_error_means)

boxplot(Sum_Errors,col = c(palette_4[1],palette_4[3],palette_4[4],palette_4[2]),
        main = "Sum of Squares Error for Parameterized Models",ylab="SSE")

error_box_plot <- function(){
MSEs <- subset[,c("und10_model1_MSE","und10_model2_MSE",
                            "und10_model3_MSE","und10_model4_MSE")]
colnames(MSEs) <-  c("y = ae^(-bx)","y = k/x^2","y =ax^(-b)","y =ke^(-kx)")
MSE_means <- colMeans(MSEs)
MSEs <- MSEs[order(MSE_means)] 
MSE_means <- MSE_means[order(MSE_means)]
print("MSE means by group")
print(MSE_means)
par(mfrow = c(1,2),mar = c(4, 4, 2, 0.5), oma = c(0, 0, 0, 0),las = 1)
boxplot(MSEs[,1:2],col = 'grey',
        main = "Two Parameter",ylab="MSE",ylim= c(0,0.012))
boxplot(MSEs[,3:4],col = 'grey',
        main = "One Parameter",ylim= c(0,0.012))
}
ggdraw(error_box_plot)
```

## Is there really a difference due to urbanization?
 
```{r}
dat_sum_under10_nobump <- dat_sum_under10_nobump %>%
  mutate(log_pop_density = log(pop_density))

```


```{r}
dat_sum_under10_metro <- dat_sum_under10_nobump[dat_sum_under10_nobump$urban_cat == "Metro",]
dat_sum_under10_micro <- dat_sum_under10_nobump[dat_sum_under10_nobump$urban_cat == "Micro",]
dat_sum_under10_rural <- dat_sum_under10_nobump[dat_sum_under10_nobump$urban_cat == "Rural",]


Metro_means <- dat_sum_under10_metro %>%
  group_by(age_cat,age_midpoint) %>%
  summarise(means = mean(rsv_proportion))

Metro_medians <- dat_sum_under10_metro %>%
  group_by(age_cat,age_midpoint) %>%
  summarise(medians = median(rsv_proportion))


Micro_means <- dat_sum_under10_micro %>%
  group_by(age_cat,age_midpoint) %>%
  summarise(means = mean(rsv_proportion))

Micro_medians <- dat_sum_under10_micro %>%
  group_by(age_cat,age_midpoint) %>%
  summarise(medians = median(rsv_proportion))


rural_means <- dat_sum_under10_rural %>%
  group_by(age_cat,age_midpoint) %>%
  summarise(means = mean(rsv_proportion))

rural_medians <- dat_sum_under10_rural %>%
  group_by(age_cat,age_midpoint) %>%
  summarise(medians = median(rsv_proportion))

means <- merge(Metro_means,Micro_means,by=c("age_cat","age_midpoint")) 
means <- merge(means,rural_means, by= c("age_cat","age_midpoint"))
means <- means[,-2]
row.names(means) <- means[,1]
means <- means[,-1]
means<- apply(t(means),2,rev)
means <- means[c(3,2,1),]
row.names(means) <- c("Metro","Micro","Rural")

barplot(means,beside = TRUE,legend.text = TRUE,
                       ylim = c(0,0.8),
                       main = "Mean Proportion of Cases per Age Category by Urban Category",
                       col = c(palette_4[2],palette_4[3],palette_4[4]),
                       xlab = "Age Category",
                       ylab = "Proportion of Cases")

medians <- merge(Metro_medians,Micro_medians,by=c("age_cat","age_midpoint"))
medians <- merge(medians,rural_medians,by=c("age_cat","age_midpoint"))
medians <- medians[,-2]
row.names(medians) <- medians[,1]
medians <- medians[,-1]
medians<- apply(t(medians),2,rev)
medians <- medians[c(3,2,1),]
row.names(medians) <- c("Metro","Micro","Rural")

barplot(medians,beside = TRUE,legend.text = TRUE,
                       ylim = c(0,0.8),
                       main = "Median Proportion of Cases per Age Category by Urban Category",
                       col = c(palette_4[2],palette_4[3],palette_4[4]),
                       xlab = "Age Category",
                       ylab = "Proportion of Cases")
```

```{r}
dat_sum_under10_nobump <- dat_sum_under10_nobump %>%
  mutate(age_cat = as.factor(age_cat))

urban_box_plot <-dat_sum_under10_nobump %>%
  ggplot(aes(x=age_cat,y = rsv_proportion)) +
  geom_boxplot(aes(fill = urban_cat),position = "dodge") +
  scale_fill_manual(values=c(palette_4[1],palette_4[3],palette_4[4]))+
  labs(x="Age Category",
       y="Proportion of RSV Cases",,
       fill = "Urban Cat.")+
  theme(plot.background = element_blank(), 
    panel.background = element_blank(), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line.x = element_line(color = "grey", size = 0.5),
    axis.line.y = element_line(color = "grey", size = 0.5),
    legend.position = c(0.9, 0.5),
    legend.box.background = element_rect(color = "grey", size = 0.5))


print(urban_box_plot)

```

## GLM 
```{r}
### binomial
mod <- glm(
  cbind(rsv.sum, rsv.total - rsv.sum) ~ age_cat * urban_cat,
  family = quasibinomial(link = "logit"),
  data = hosp_data_nobump
)
summary(mod)

stargazer(mod)
```

## GAM


```{r}
hist(hosp_data_nobump$und10_model1_b)

b_GAM <-gam(und10_model1_b ~ s(avg_humid, k = 5)+s(log_pop_density),data = hosp_data_nobump)
b_GAM_combine <-gam(und10_model1_b ~ s(avg_humid,log_pop_density),data = hosp_data_nobump)

anova(b_GAM,b_GAM_combine,test = 'F')

summary(b_GAM)
summary(b_GAM_combine)
```

```{r}
hist(hosp_data_nobump$und10_model4_k)

k_GAM <-gam(und10_model4_k ~ s(avg_humid, k = 5)+s(log_pop_density),data = hosp_data_nobump)
k_GAM_combine <-gam(und10_model4_k ~ s(avg_humid,log_pop_density),data = hosp_data_nobump)

anova(k_GAM,k_GAM_combine,test = 'F')

summary(k_GAM)
summary(k_GAM_combine)
```




## Model fits by urban category
```{r}

mean_plot_b <- function(){
    x <- dat_sum_under10_metro$age_midpoint
    y <- dat_sum_under10_metro$rsv_proportion
    
    # fit to y = a*e^(bx) 
    start_values <- c(a=1, b=1)
    fit <- nls(y ~ a * exp(-b * x),
           start = start_values,
           algorithm = "port",
           control = nls.control(maxiter = 1000))
    fit_coef <- coef(fit)
    metro_a <- fit_coef["a"]
    metro_b <- fit_coef["b"]
    
    x <- dat_sum_under10_micro$age_midpoint
    y <- dat_sum_under10_micro$rsv_proportion
    
    # fit to y = a*e^(bx) 
    start_values <- c(a=1, b=1)
    fit <- nls(y ~ a * exp(-b * x),
           start = start_values,
           algorithm = "port",
           control = nls.control(maxiter = 1000))
    fit_coef <- coef(fit)
    micro_a <- fit_coef["a"]
    micro_b <- fit_coef["b"]
    
    x <- dat_sum_under10_rural$age_midpoint
    y <- dat_sum_under10_rural$rsv_proportion
    
    # fit to y = a*e^(bx) 
    start_values <- c(a=1, b=1)
    fit <- nls(y ~ a * exp(-b * x),
           start = start_values,
           algorithm = "port",
           control = nls.control(maxiter = 1000))
    fit_coef <- coef(fit)
    rural_a <- fit_coef["a"]
    rural_b <- fit_coef["b"]
    

ages <- seq(0, 5, length.out = 100) 
metro_predict <-  metro_a* exp( -metro_b * ages)
micro_predict <-  micro_a* exp(- micro_b * ages)
rural_predict <-  rural_a* exp( -rural_b * ages)
par(mar = margin_try1,las = 1)
plot(Metro_means$age_midpoint[1:5],Metro_means$means[1:5], col = palette_4[1],pch = 19,cex =1.5,ylab = " ", main = " ",xlab = " ",bty = 'l')
points(Micro_means$age_midpoint[1:5],Micro_means$means[1:5], col = palette_4[3],pch = 19,cex =1.5)
points(rural_means$age_midpoint[1:5],rural_means$means[1:5], col = palette_4[4],pch = 19,cex =1.5)
lines(ages,metro_predict,col = palette_4[1],lty  = "dashed",lwd = 2)
lines(ages,micro_predict,col = palette_4[3],lty  = "dashed",lwd = 2)
lines(ages,rural_predict,col = palette_4[4],lty  = "dashed",lwd = 2)
legend("topright",legend = c(sprintf("Metro (b = %.2f)", metro_b),
                             sprintf("Micro (b = %.2f)", micro_b),
                             sprintf("Rural (b = %.2f)", rural_b)),
       col = c(palette_4[1],palette_4[3],palette_4[4]),lty=2, cex=1,lwd =2)
}

mean_plot_k <- function(){
    x <- dat_sum_under10_metro$age_midpoint
    y <- dat_sum_under10_metro$rsv_proportion
    
    # fit to y = ke^(-kx)
    start_values <- c(k = 2)
    fit <- nls(y ~ k* exp(-k * x),
           start = start_values,
           algorithm = "port",
           control = nls.control(maxiter = 1000))
    fit_coef <- coef(fit)
    metro_k <- fit_coef["k"]
    
    x <- dat_sum_under10_micro$age_midpoint
    y <- dat_sum_under10_micro$rsv_proportion
    
    # fit to y = ke^(-kx)
    start_values <- c(k = 2)
    fit <- nls(y ~ k* exp(-k * x),
           start = start_values,
           algorithm = "port",
           control = nls.control(maxiter = 1000))
    fit_coef <- coef(fit)
    micro_k <- fit_coef["k"]
    
    x <- dat_sum_under10_rural$age_midpoint
    y <- dat_sum_under10_rural$rsv_proportion
    
    # fit to y = ke^(-kx)
    start_values <- c(k = 2)
    fit <- nls(y ~ k* exp(-k * x),
           start = start_values,
           algorithm = "port",
           control = nls.control(maxiter = 1000))
    fit_coef <- coef(fit)
    rural_k <- fit_coef["k"]
    

ages <- seq(0.4, 5, length.out = 100) 
metro_predict <-  metro_k* exp( -metro_k * ages)
micro_predict <-  micro_k* exp(- micro_k * ages)
rural_predict <-  rural_k* exp( -rural_k * ages)
par(mar = margin_try2,las = 1)
plot(Metro_means$age_midpoint[1:5],Metro_means$means[1:5], col = palette_4[1],pch = 19,cex =1.5,xlab= "Age",ylab = " ",bty = 'l')
points(Micro_means$age_midpoint[1:5],Micro_means$means[1:5], col = palette_4[3],pch = 19,cex =1.5)
points(rural_means$age_midpoint[1:5],rural_means$means[1:5], col = palette_4[4],pch = 19,cex =1.5)
lines(ages,metro_predict,col = palette_4[1],lty  = "dashed",lwd = 2)
lines(ages,micro_predict,col = palette_4[3],lty  = "dashed",lwd = 2)
lines(ages,rural_predict,col = palette_4[4],lty  = "dashed",lwd = 2)
legend("topright",legend = c(sprintf("Metro (k = %.2f)", metro_k),
                             sprintf("Micro (k = %.2f)", micro_k),
                             sprintf("Rural (k = %.2f)", rural_k)),
       col = c(palette_4[1],palette_4[3],palette_4[4]),lty=2, cex=1,lwd =2)
}

```

```{r}
margin_try1 <-c(2, 4.1, 2.1, 2.1)
margin_try2 <-c(4.1, 4.1, 0, 2.1)
combined_plots <- plot_grid(mean_plot_b,mean_plot_k,ncol = 1, rel_heights = c(1, 1))
mean_plots <- ggdraw() +
  draw_plot(combined_plots) +
  draw_label("Proportion of RSV Cases", 
             angle = 90, 
             size = 14, 
             x = 0.025,  
             y = 0.5,   
             hjust = 0.5, 
             vjust = 0.5)
print(mean_plots)
```


## Connecting to humidity data

```{r}
hosp_data_nobump <- hosp_data_nobump[order(hosp_data_nobump$log_pop_density),]
ggplot(hosp_data_nobump, aes(x = avg_humid, y = und10_model1_b, 
                             color = log_pop_density)) +
  geom_point(size = 3) +
  scale_color_distiller(palette = gradient_palette)+
  labs(x = "Average Historic Humidity", y = "Parameter b", 
       color = "Log Pop. Density", title = "y = a e^(-b x)")

ggplot(hosp_data_nobump, aes(x = avg_humid, y = und10_model1_b, 
                             color = log_pop_density)) +
  geom_point(size = 3) +
  scale_color_distiller(palette = gradient_palette) +
  labs(x = "Avg. Humidity", y = "b", color = "Log Pop. Density",
       title = "y = a e^(-b x)")+
  geom_smooth(data = hosp_data_nobump, aes(x = avg_humid, y =und10_model1_b), 
              method = "lm", se = FALSE, color = "black",linetype="dashed")
hosp_data_nobump <- hosp_data_nobump[order(hosp_data_nobump$avg_humid),]
ggplot(hosp_data_nobump, aes(x = log_pop_density, y = und10_model1_b, 
                             color = avg_humid)) +
  geom_point(size = 2) +
  scale_color_distiller(palette = gradient_palette) +
  labs(x = "Log Pop. Density", y = "b", color = "Average Historic Humidity",
       title = "y = a e^(-b x)")
bottom_row_b <- ggplot(hosp_data_nobump, aes(x = log_pop_density, y = und10_model1_b,
                             color = avg_humid)) +
  geom_point(size = 2) +
  scale_color_distiller(palette = gradient_palette) +
  labs(x = "Log Pop. Density", y = "b", color = "Avg. Humidity",
       title = "    y = a e^(-b x)")+
  geom_smooth(data = hosp_data_nobump, aes(x = log_pop_density, y =und10_model1_b), 
              method = "lm", se = FALSE, color = "black",linetype="dashed")+
  theme(plot.background = element_blank(), 
    panel.background = element_blank(),
    axis.line.x = element_line(color = "grey", size = 0.5),
    axis.line.y = element_line(color = "grey", size = 0.5),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.key.size = unit(0.6, "cm"),      
    legend.key.width = unit(0.3, "cm"),     
    legend.text = element_text(size = 8),   
    legend.title = element_text(size = 9))  
print(bottom_row_b)

humid_b_lm <- lm(hosp_data_nobump$und10_model1_b ~ hosp_data_nobump$avg_humid)
logpopdens_b_lm <- lm(hosp_data_nobump$und10_model1_b ~ hosp_data_nobump$log_pop_density)
summary(humid_b_lm)
summary(logpopdens_b_lm)
```


```{r} 
hosp_data_nobump <- hosp_data_nobump[hosp_data_nobump$und10_model4_k<4,]
hosp_data_nobump <- hosp_data_nobump[order(hosp_data_nobump$log_pop_density),]
ggplot(hosp_data_nobump, aes(x = avg_humid, y = und10_model4_k, 
                             color = log_pop_density)) +
  geom_point(size = 3) +
  scale_color_distiller(palette = gradient_palette) +
  labs(x = "Avg.Humidity", y = "Parameter k", color = "Log Pop. Density",
       title = "y =k e^(-kx)")
ggplot(hosp_data_nobump, aes(x = avg_humid, y = und10_model4_k, 
                             color = log_pop_density)) +
  geom_point(size = 3) +
  scale_color_distiller(palette = gradient_palette) +
  labs(x = "Avg. Humidity", y = "Parameter k", color = "Log Pop. Density",
       title = "y =k e^(-kx)")+
  geom_smooth(data = hosp_data_nobump, aes(x = avg_humid, y =und10_model4_k), 
              method = "lm", se = FALSE, color = "black", linetype="dashed")
hosp_data_nobump <- hosp_data_nobump[order(hosp_data_nobump$avg_humid),]
ggplot(hosp_data_nobump, aes(x = log_pop_density, y = und10_model4_k, color = avg_humid)) +
  geom_point(size = 3) +
  scale_color_distiller(palette = gradient_palette) +
  labs(x = "Log Pop. Density", y = "Parameter k", color = "Avg. Humidity",
       title = "y =k e^(-kx)")
bottom_row_k <- ggplot(hosp_data_nobump, aes(x = log_pop_density, y = und10_model4_k, color = avg_humid)) +
  geom_point(size = 2) +
  scale_color_distiller(palette = gradient_palette) +
  labs(x = "Log Pop. Density", y = "k", color = "Avg.  Humidity",
       title = "y =k e^(-kx)")+
  geom_smooth(data = hosp_data_nobump, aes(x = log_pop_density, y =und10_model4_k),
              method = "lm", se = FALSE, color = "black", linetype="dashed")+
  theme(plot.background = element_blank(), 
    panel.background = element_blank(),
    axis.line.x = element_line(color = "grey", size = 0.5),
    axis.line.y = element_line(color = "grey", size = 0.5),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())
print(bottom_row_k)

humid_k_lm <- lm(hosp_data_nobump$und10_model4_k ~ hosp_data_nobump$avg_humid)
logpopdens_k_lm <- lm(hosp_data_nobump$und10_model4_k ~ hosp_data_nobump$log_pop_density)
summary(humid_k_lm)
summary(logpopdens_k_lm)
```



## Mapping by parameter

```{r}
hosp_data_cuttoff <- hosp_data_nobump[hosp_data_nobump$und10_model1_b<2.5 & hosp_data_nobump$und10_model4_k<2.5,]
hosp_data_cuttoff <- hosp_data_cuttoff[hosp_data_cuttoff$und10_model4_k>0.5,]
hosp_data_cuttoff <- hosp_data_cuttoff[order(hosp_data_cuttoff$und10_model1_b,decreasing = FALSE),]
usa_map <- map_data("usa")
library(pals)
map_plot1 <- ggplot() +
  geom_polygon(data=usa_map,aes(x=long,y=lat,group=group),fill = '#434343',color ='#434343')+
  geom_point(data = hosp_data_cuttoff,aes(x=longitude,y =latitude,color = und10_model1_b),size=1.8)+
  labs(color = "b")+
  scale_color_distiller(palette = "RdBu",
                        values=scales::rescale(c(0, 0.4, 0.6, 1)),
                        guide = guide_colorbar(barheight = 0.7))+
  theme_minimal()+
  theme(axis.title = element_blank(),
    axis.text = element_blank(),        
    axis.ticks = element_blank(),
    panel.grid = element_blank(),
    legend.position = "none")
#############
legend_plot <- ggplot() +
  geom_point(data = hosp_data_cuttoff, aes(x = longitude, y = latitude, color = und10_model1_b), size = 1.8) +
  scale_color_distiller(name = "b",palette = "RdBu",
                        values = scales::rescale(c(0, 0.4, 0.6, 1)),
                        guide = guide_colorbar(barheight = 10,
                                               barwidth = 0.8)) +
  theme_minimal() +
  theme(legend.position = "right")
legend_onlyb <- plot_grid(get_legend(legend_plot),rel_heights = c(1))
print(legend_onlyb)
##############

hosp_data_cuttoff <- hosp_data_cuttoff[order(hosp_data_cuttoff$und10_model4_k,decreasing = FALSE),]

map_plot2 <- ggplot() +
  geom_polygon(data=usa_map,aes(x=long,y=lat,group=group),fill = '#434343',color ="#434343")+
  geom_point(data = hosp_data_cuttoff,aes(x=longitude,y =latitude,color=und10_model4_k),size=1.8)+
  labs(color = "k")+
  scale_color_distiller(palette = "RdBu",
                        values=scales::rescale(c(0, 0.4, 0.6, 1)),
                        guide = guide_colorbar(barheight = 0.7))+
  theme_minimal()+
  theme(axis.title = element_blank(),
    axis.text = element_blank(),        
    axis.ticks = element_blank(),
    panel.grid = element_blank(),
    legend.position = "none")
################
legend_plot <- ggplot() +
  geom_point(data = hosp_data_cuttoff, aes(x = longitude, y = latitude, color = und10_model4_k), size = 1.8) +
  scale_color_distiller(name = "k",palette = "RdBu",
                        values = scales::rescale(c(0, 0.4, 0.6, 1)),
                        guide = guide_colorbar(barheight = 10,
                                               barwidth = 0.8)) +
  theme_minimal() +
  theme(legend.position = "right")
legend_onlyk <- plot_grid(get_legend(legend_plot),rel_heights = c(1))
print(legend_onlyk)
################
print(map_plot1)
print(map_plot2)
hist((hosp_data_cuttoff$und10_model1_b))
hist((hosp_data_cuttoff$und10_model4_k))
```




## Linear models, Fitted parameters vs urban_cat
Here we look at the fitted parameters for under10 for model 1 and 4
- linear models on the fitted parameters

```{r}
lm1_und10_b_popdens <- lm(und10_model1_b~log_pop_density,data = hosp_data_nobump)
lm5_und10_k_popdens <- lm(und10_model4_k~log_pop_density,data = hosp_data_nobump)
lm1_und10_b_humid <- lm(und10_model1_b~avg_humid,data = hosp_data_nobump)
lm5_und10_k_humid <- lm(und10_model4_k~avg_humid,data = hosp_data_nobump)
print(summary(lm1_und10_b_popdens))
print(summary(lm1_und10_b_humid))
print(summary(lm5_und10_k_popdens))
print(summary(lm5_und10_k_humid))

```
> Linear models provide similar error/outputs across log_pop and log_pop_density. Not much difference indicates using log_pop is a sufficient metric vs. log_pop_density.

```{r}

und10_b_combined <- lm(und10_model1_b~log_pop_density +avg_humid,data = hosp_data_nobump)

print(summary(und10_b_combined))

und10_k_combined <- lm(und10_model4_k~log_pop_density +avg_humid, data = hosp_data_nobump)

print(summary(und10_k_combined))
```

> log_pop_dens is a more important predictor than avg_humidity.

```{r}
colors <- c("Uni y = ke^(-kx)" = palette_4[2],"Uni y = ae^(-bx)" = palette_4[1],"Multi y = ke^(-kx)" = palette_4[4],"Multi y = ae^(-bx)" = palette_4[3])

combined_b <- tidy(und10_b_combined)
combined_b <- combined_b %>%
  mutate(model = "Multi y = ae^(-bx)")
humid_combined_b <- combined_b[combined_b$term == 'avg_humid',]
pop_dens_combined_b <- combined_b[combined_b$term == 'log_pop_density',]

combined_k <- tidy(und10_k_combined)
combined_k <- combined_k %>%
  mutate(model = "Multi y = ke^(-kx)")
humid_combined_k <- combined_k[combined_k$term == 'avg_humid',]
pop_dens_combined_k <- combined_k[combined_k$term == 'log_pop_density',]

pop_dens_k <- tidy(lm5_und10_k_popdens)
pop_dens_k <- pop_dens_k %>%
  mutate(model = "Uni y = ke^(-kx)")
pop_dens_b <- tidy(lm1_und10_b_popdens)
pop_dens_b <- pop_dens_b %>%
  mutate(model = "Uni y = ae^(-bx)")
pop_dens <- bind_rows(pop_dens_b,pop_dens_k)
pop_dens <- bind_rows(pop_dens,pop_dens_combined_b)
pop_dens <- bind_rows(pop_dens,pop_dens_combined_k)



humid_k <- tidy(lm5_und10_k_humid)
humid_k <- humid_k %>%
  mutate(model = "Uni y = ke^(-kx)")
humid_b <- tidy(lm1_und10_b_humid)
humid_b <- humid_b %>%
  mutate(model = "Uni y = ae^(-bx)")
humid <- bind_rows(humid_b,humid_k)
humid <- bind_rows(humid,humid_combined_b)
humid <- bind_rows(humid,humid_combined_k)

plot1 <- dwplot(pop_dens)+
  labs(title = "",x = "b/k")+
  theme(axis.text.y = element_blank(),        
    axis.ticks.y = element_blank(),
    plot.background = element_blank(), 
    panel.background = element_blank(), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line.x = element_line(color = "grey", size = 0.5),
    legend.position="none")+
  scale_color_manual(values = colors,name = "Model")+
  scale_x_continuous(limits = c(-0.008, NA)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "#939393", size = 0.6)

plot2 <- dwplot(humid)+
  labs(title = "",x = "b/k")+
  theme(axis.text.y = element_blank(),        
    axis.ticks.y = element_blank(),
    plot.background = element_blank(), 
    panel.background = element_blank(), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line.x = element_line(color = "grey", size = 0.5),
    legend.position="none")+
  scale_color_manual(values = colors,name = "Model")+
  # scale_x_continuous(limits = c(0, NA)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "#939393", size = 0.6)
# Combine the plots vertically


pop_dens <- pop_dens[c(2,5),]
humid <- humid[c(4,6),]

## Make plots just so that legend looks nice
plot3 <- dwplot(pop_dens)+
  labs(title = "Log Pop. Density",x = "b/k")+
  theme(axis.text.y = element_blank(),        
    axis.ticks.y = element_blank(),legend.position = "bottom",
    plot.background = element_blank(), 
    panel.background = element_blank(), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line.x = element_line(color = "grey", size = 0.5))+
  scale_color_manual(values = colors,name = "")+
  scale_x_continuous(limits = c(0, NA)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "#939393", size = 0.6)
plot4 <- dwplot(humid)+
  labs(title = "Log Pop. Density",x = "b/k")+
  theme(axis.text.y = element_blank(),        
    axis.ticks.y = element_blank(),legend.position = "bottom",
    plot.background = element_blank(), 
    panel.background = element_blank(), 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line.x = element_line(color = "grey", size = 0.5))+
  scale_color_manual(values = colors,name = "")+
  scale_x_continuous(limits = c(0, NA)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "#939393", size = 0.6)
legendtop <- get_plot_component(plot3, 'guide-box-bottom', return_all = TRUE)
legendbottom <- get_plot_component(plot4, 'guide-box-bottom', return_all = TRUE)

legends <- plot_grid(legendtop,legendbottom, ncol = 1, align = 'v')
```

## Parameter statistical test by urban_cat
ANOVA testing
Let $\mu_{\text{cat}}$ be the mean of a parameter of a given urban_cat.

$$H_0: \mu_{\text{Metro}}=\mu_{\text{Micro}}=\mu_{\text{Rural}}$$

$$H_1: \text{at least one mean is different.}$$
```{r}
hosp_data_nobump %>%
  group_by(urban_cat) %>%
  summarise(mean_a = mean(und10_model1_a),
            sd_a = sd(und10_model1_a),
            mean_b = mean(und10_model1_b),
            sd_b = sd(und10_model1_b),
            mean_k = mean(und10_model4_k),
            sd_k = sd(und10_model4_k))
```


```{r}
Anova_model1b <- aov(und10_model1_b ~ urban_cat, data = hosp_data_nobump)
  print(summary(Anova_model1b))
  print(TukeyHSD(Anova_model1b))
  
Anova_model4k <- aov(und10_model4_k ~ urban_cat, data = hosp_data_nobump)
  print(summary(Anova_model4k))
  print(TukeyHSD(Anova_model4k))
```
> All pairings of the parameters are statistically significant.


