---
title: "Vaccination"
author: "Presley Kimball"
date: "2024-06-27"
output: html_document
---

## Set up
```{r}
library(readxl)
library(tidyverse)
library(dplyr)
library(deSolve)
library(RColorBrewer)
library(ggplot2)
library(lhs)
library(colorspace)

# set your working directory to be the overall file folder
setwd("FILLIN")

# set color palettes
palette_4 <- brewer.pal(4, "Spectral") 
palette_5 <- rev(brewer.pal(9, "YlGnBu")[c(3:6,8)])
palette_6 <- rev(brewer.pal(9, "YlGnBu")[c(3:8)])
palette_11 <- colorspace::sequential_hcl(11)
```
## Bringing in Texas Data
```{r}
# load in Texas data
load("data/TexasData/TX_pop_size.RData")

# # load rural data
load("data/TexasData/TX_rural_pop_size.RData")
```

## Load in contact matrix and correct the format
```{r}
# Call in contact matrix
K <- read_excel("/data/US_contact.xlsx")
K <- as.matrix(K)
# duplicate the first column (match other age groups)
K <- cbind(K[,1],K[,1],K[,1],K[,1],K)
K <- rbind(K[1,],K[1,],K[1,],K[1,],K)
colnames(K) <- c("0-1","1-2","2-3","3-4","4-5","5-10", "10-15", "15-20", "20-25",
                 "25-30", "30-35", "35-40", "40-45", "45-50", "50-55", "55-60",
                 "60-65", "65-70", "70-75", "75+")
rownames(K) <- c("0-1","1-2","2-3","3-4","4-5","5-10", "10-15", "15-20", "20-25",
                 "25-30", "30-35", "35-40", "40-45", "45-50", "50-55", "55-60",
                 "60-65", "65-70", "70-75", "75+")

# transpose the matrix to match interpretation of main manuscript
K <- t(K)
```

## Setting Global Parameters
We will use the general age distribution of the US census in 2010.
\url{https://www.census.gov/content/dam/Census/library/publications/2011/dec/c2010br-03.pdf}
```{r}
N0_ages <- c("0-1"= 20201362/5,
            "1-2" = 20201362/5,
            "2-3" = 20201362/5,
            "3-4" = 20201362/5,
            "4-5" = 20201362/5,
            "5-10" = 20348657,
            "10-15" = 20677194,
            "15-20" = 22040343,
            "20-25" = 21585999,
            "25-30" = 21101849,
            "30-35" = 19962099,
            "35-40" = 20179642,
            "40-45" = 20890964,
            "45-50" = 22708591,
            "50-55" = 22298125,
            "55-60" = 19664805,
            "60-65" = 16817924,
            "65-70" = 12435263,
            "70-75" = 9278166,
            "75+" = 7317795+5743327+3620459+1448366+371244+53364)

# Set global variables. Note all rates are by week
Lambda = c("0-1"=(385746/25145561)/365.25*7,"1-2" = 0,"2-3" = 0,"3-4" = 0,"4-5" = 0,
           "5-10" = 0,"10-15" = 0,"15-20" = 0,"20-25" = 0,"25-30" = 0,"30-35" = 0,
           "35-40" = 0,"40-45" = 0,"45-50" = 0,"50-55" = 0,"55-60" = 0,"60-65" = 0,
           "65-70" = 0,"70-75" = 0,"75+" = 0)
mu = (385746/25145561)/365.25*7
ages <- c(0:4,seq(5,75,by=5))
T <- length(ages)
age_cats <- c("0-1","1-2","2-3","3-4","4-5","5-10", "10-15", "15-20", "20-25",
              "25-30", "30-35", "35-40", "40-45", "45-50", "50-55", "55-60",
              "60-65", "65-70", "70-75", "75+")
m = 1/200*7
gamma_vec = c(1/10,1/7,1/5,1/5)*7
r_vec = c(1/(diff(ages)*365.25),0)*7
rho_vec = c(1,0.75,0.51,0.51)
sigma_vec = c(1,0.76,0.6,0.4)
p_R = 1
K = K
h_1 = c((0.2*0.44*0.9/4+0.08*0.43*0.9/4+0.07*0.23*0.9/4+0.06*0.22*0.9/4*2),# 0-1
        0.06*0.21*0.8,# 1-2
        0.05*0.2*0.8,# 2-3
        0.05*0.2*0.8,#3-4
        0.05*0.2*0.8,#4-5
        0.05*0.2*0.8,#5-10
        rep(0.02*0.05,length(ages)-6)# above 5
        )
h_2 = 0.4*h_1
h_3 = rep(0,length(ages))# set to zero, maybe close to 0 would be better
nu_m <- (1/6)*(12*7/365.25)
nu_b <- (1/5)*(12*7/365.25)
iota_m <- 1-0.57
iota_b <- 1-0.8
year_round_vacc = FALSE
```

## General setup
```{r}
StateNames <- c('S0','S1','S2','S3','I1','I2','I3','I4','R','Vm','Vb')
States <- array(NA, dim=c(length(ages), length(StateNames) )) 
dimnames(States)[[1]] <- age_cats
dimnames(States)[[2]] <- StateNames

States_IC <- States

States_IC[,c('S1','S2','S3','I2','I3','I4','R','Vm','Vb')]  = 0
States_IC[,'S0'] = c(N0_ages[1:nrow(States_IC)])
States_IC[,'I1'] = c(rep(10000,nrow(States_IC)))  #initializes with 10000 infected person per age group (This is since the N0_ages values are based on entire US population. We rescale down to population being simulated later. This allows for base epidemic to occur.)

# Scale total population size down to 1 (so that the population size is stable)
# We are assuming that all locations have similar population distribution and 
# thus are rescaled by the population in each location (done later)
States_IC <- States_IC/sum(States_IC)

# convert initial condition to a vector for ODE solver
States_IC_vec <- as.vector(States_IC)
names(States_IC_vec) <- paste(rep(rownames(States_IC),ncol(States_IC)),
                              rep(colnames(States_IC),each = nrow(States_IC)), sep = " ")
```

## Tau vector function
Function that calculates the tau vector based on two inputs:
$$\tau = \tau_1*(\text{age_midpoints})+\tau_2$$ only for first five age_categories
```{r}
tau_vec <- function(tau_1,tau_2){
  tau <- rep(1,length(age_cats))
  for(i in 1:5){
    tau[i] <- tau_1 * ((i-1)+0.5)+tau_2
  }
  return(tau)
}
```

## Call in source files
```{r}
source('source/SIR.R')
source('source/Track_Hospitalizations.R')
source("source/Vacc_Sim.R")
source('source/Coverage_per_time.R')
```

## load in base parameters to use in SIR model
```{r}
# only want one set of parameters fro now, so delete all others
load("output/TX_parms.RData")
parms <- TX_parms[[4]][1,]
rm(TX_parms)
# run vaccination on base params
```


```{r}
# set coverage rate and run model
chis <- seq(0,1,0.1)
taus <- c(1,1.25,0.75)

for (tau in taus){
  if (tau == 1){
    fig_ind <- 1
  }
  if (tau == 0.75) {
    fig_ind <- 3
  }
  if (tau == 1.25){
    fig_ind <- 2
  }
  output <- Vacc_Sim(parms, 0,tau,5,10,chis)

  # store model outputs
  under1 <- output[[1]]
  total_hosp <- output[[2]]
  prop_coverage <- output[[3]]
  max_peak <- output[[4]]
  
  # # plot outputs
  par(mar = c(5.1, 4.1, 4.1, 2.1),  mgp = c(3, 1, 0))
  plot(total_hosp[,1],total_hosp[,2]*TX_pop_size,
       xlim = c(0,max(total_hosp[,1])),
       ylim = c(0,max(total_hosp[,2:ncol(total_hosp)])*TX_pop_size),
       type = 'l', lwd = 2,col = palette_6[1],
       main = paste(tau,": Total Hospitalizations"),xlab = "Weeks",
       ylab = "Hospitalizations")
  for(i in 1:2){
    j <- c(6,10)[i]
    k <- c(5,6)[i]
    lines(total_hosp[,1],total_hosp[,j+1]*TX_pop_size, col = palette_6[k],lwd = 2)
    }
  legend("topleft", legend=chis[c(1,6,10)],
         col=palette_6[c(1,5,6)], lty=1,lwd = 2, cex=0.8,
         title="Coverage Rate", text.font=4)
  par(mar = c(5.1, 4.1, 4.1, 2.1),  mgp = c(3, 1, 0))
  plot(under1[,1],under1[,2]*TX_pop_size,
       xlim = c(0,max(under1[,1])),
       ylim = c(0,max(under1[,2:ncol(total_hosp)])*TX_pop_size),
       type = 'l', lwd = 2,col = palette_6[1],
       main = paste(tau,":under 1"),xlab = "Weeks", ylab = "Hospitalizations")
  for(i in 1:5){
    j <- c(3,5,7,9,11)[i]
    lines(under1[,1],under1[,j+1]*TX_pop_size, col = palette_6[i+1],lwd = 2)
    }
  legend("bottomleft", legend=chis[c(1,3,5,7,9,11)],
         col=palette_6, lty=1,lwd = 2, cex=0.8,
         title="Coverage Rate", text.font=4)

  # make bar plots of outputs
  hosps <- prop_coverage/(max(rowSums(prop_coverage)))
  hosps_under10 <- hosps[,1:7]
  hosps_under10[,7] = rowSums(prop_coverage[,1:6])/(max(rowSums(prop_coverage[,1:6])))
  colnames(hosps_under10) <- c(colnames(hosps_under10[,1:6]),"total")
  hosps_under10 <- hosps_under10[,c(7,1:6)]
  if (tau == 1){

    barplot(hosps_under10, beside= TRUE, legend = TRUE,
          col = palette_11,
          main = paste("RSV Cases for Varying Coverage Rates"),
          xlab = "Age Category",
          ylab = "Standardized Hospitalizations")

  }
  barplot(hosps_under10, beside= TRUE, legend = TRUE,
          col = palette_11,
          main = paste(tau,": RSV Cases for Varying Coverage Rates"),
          xlab = "Age Category",
          ylab = "Standardized Hospitalizations")

    infect_cov = rowSums(hosps)
  par(mar = c(1.5, 1.5, 0.1, 0.1),mgp = c(1.5,0.5,0))
  plot(chis,infect_cov,main = "",
       xlab = "",ylab = "", type = 'l',
       ylim = c(0,1),lwd = 2,bty ='l',asp = 1)
  for(i in 1:5){
    lines(chis,hosps[,i],col = palette_5[i],lwd = 2)
  }
  par(pty = "s")
  plot(chis,infect_cov,main = paste(tau,": Coverage Rate vs Hospitalizations"),
       xlab = "Coverage Rate",ylab = "RSV Cases", type = 'l',
       ylim = c(0,1),lwd = 2,bty ='l',asp = 1)
  for(i in 1:6){
    lines(chis,hosps[,i],col = palette_6[i],lwd = 2)
  }
  legend("bottomleft",legend = c("Total",age_cats[1:6]),col = c('black',palette_6),lty = 1,lwd = 2,cex = 0.6)

  max_age_cov <- as.data.frame(matrix(nrow = length(chis),ncol = length(age_cats)))
  row.names(max_age_cov) <- chis
  colnames(max_age_cov) <- c("total",age_cats[1:(length(age_cats)-1)])

  for (i in 1:length(max_peak)){
    mat <- max_peak[[i]]
    mat <- apply(mat, 2, as.numeric)
    mat_max <- apply(mat, 2, max)
    total <- max(rowSums(mat[,2:ncol(mat)]))
    max_age_cov[i,] <- c(total,mat_max[2:length(mat_max)])
  }
  # # standardize here
  if (tau == 1){
    # standard_max <- max_age_cov[1,1]
    under1_max <- max_age_cov[1,2]
  }
  standard_max <- max_age_cov[1,1]
  max_age_cov <- max_age_cov/standard_max

    par(mar = c(1.5, 1.5, 0.1, 0.1),mgp = c(1.5,0.5,0))
    plot(chis,max_age_cov[,1], type = 'l', lwd = 2,
             ylim = c(0,1.16),
             ylab = "",
             xlab = "",
             main = "",
             bty ='l')
        for (i in 1:5){
          lines(chis,max_age_cov[,i+1], lwd = 2, col = palette_5[i])
        }
  legend("bottomright",legend = c("Total",age_cats[1:5]),col = c('black',palette_5),lty = 1,lwd = 2,cex = 0.7,bg ='white')

  
  # ### shift in timing
    last_year_index <- total_hosp[,1]>(max(total_hosp[,1])-(365.25/7))
    last_year_hosps <- total_hosp[last_year_index,]
    outbreak_week <- rep(NA,length.out = length(chis))
    for (i in 2:ncol(last_year_hosps)){
      max_index <- which.max(last_year_hosps[,i])
      if (i == 2){
        rel_time <- last_year_hosps[max_index,1]
      }
      outbreak_week[i-1] <- (last_year_hosps[max_index,1] -rel_time) %% (365.25/7)
    }

      par(mar = c(1.5, 1.5, 0.1, 0.1),mgp = c(1.5,0.5,0))
      plot(chis,outbreak_week, type = 'l', lwd = 2,
                   ylab = "",
                   xlab = "",
                   main = "",
                   bty ='l', ylim = c(0,24))

    
    ### stable peak size
    stable_peaks <- matrix(NA, nrow = length(chis),ncol = 6) #nrow is chis
  for (i in 1:length(chis)){
    mat <- max_peak[[i]]
    stable_peaks[i,1] <- sum(mat[nrow(mat),2:ncol(mat)])
    stable_peaks[i,2:6] <- as.numeric(mat[nrow(mat),2:6])
  }
    stable_peaks <- stable_peaks/stable_peaks[1,1]

   par(mar = c(1.5, 1.5, 0.1, 0.1),mgp = c(1.5,0.5,0))
    plot(chis,stable_peaks[,1], type = 'l', lwd = 2,
             ylab = "",
             xlab = "",
             main = "",
             bty ='l', ylim = c(0,1.1))
        for (i in 1:5){
          lines(chis,stable_peaks[,i+1], lwd = 2, col = palette_5[i])
      }

}

  par(mar = c(0.5, 0.5, 0.5, 0.5))
  plot.new()
  legend("center",legend = c("Total",age_cats[1:5]),col = c('black',palette_5),
         lty = 1,lwd = 2,cex = 0.8,bg ='white', horiz = T)


```

# normal plots for tau=1
```{r}
colors = rev(c('#4D3ECA','#00CEA6'))
chis <- c(0,0.5,0.9)
output <- Vacc_Sim(parms, 0,1,5,15,chis)
total_hosp <- output[[2]]


indices = total_hosp[,1]>52*3 & total_hosp[,1]<11*52
  par(mar = c(0.5, 2, 1, 1), mgp = c(1.6, 0.5, 0))
  plot(total_hosp[indices,1], total_hosp[indices,2]*TX_pop_size,
       ylim = c(0,1400),bty = 'l', type ='l', lwd =2, 
       col ='grey', lty = 2,ylab = '',xlab = '',xaxt = 'n')
  for (i in 1:2){
    lines(total_hosp[indices,1], total_hosp[indices,i+2]*TX_pop_size,
       ylim = c(0,1400),bty = 'l', type ='l', lwd =2, 
       col =colors[i])
  }
  legend('topleft',title = 'Coverage Rate', legend = c(0,0.5,0.9),col = c('grey',colors),lty = c(2,1,1),lwd = 2, cex = 0.8)

year_round_vacc <- TRUE
output <- Vacc_Sim(parms, 0,1,5,15,chis)
total_hosp <- output[[2]]

indices = total_hosp[,1]>52*3 & total_hosp[,1]<11*52

  par(mar = c(2, 2, 1, 1), mgp = c(1.6, 0.5, 0))
  plot(total_hosp[indices,1], total_hosp[indices,2]*TX_pop_size,
       ylim = c(0,1400),bty = 'l', type ='l', lwd =2, 
       col ='grey', lty = 2,ylab = '',xlab = '')
  for (i in 1:2){
    lines(total_hosp[indices,1], total_hosp[indices,i+2]*TX_pop_size,
       ylim = c(0,1400),bty = 'l', type ='l', lwd =2, 
       col =colors[i])
  }
year_round_vacc <- F
```
# plots for tau =0.75
```{r}
colors = rev(c('#4D3ECA','#00CEA6'))
chis <- c(0,0.5,0.9)
output <- Vacc_Sim(parms, 0,0.75,5,15,chis)
total_hosp <- output[[2]]


indices = total_hosp[,1]>52*3 & total_hosp[,1]<11*52
  par(mar = c(0.5, 2, 1, 1), mgp = c(1.6, 0.5, 0))
  plot(total_hosp[indices,1], total_hosp[indices,2],
       ylim = c(0,1400/TX_pop_size),bty = 'l', type ='l', lwd =2, 
       col ='grey', lty = 2,ylab = '',xlab = '',xaxt = 'n')
  for (i in 1:2){
    lines(total_hosp[indices,1], total_hosp[indices,i+2],
       ylim = c(0,1400/TX_pop_size),bty = 'l', type ='l', lwd =2, 
       col =colors[i])
  }
  legend('topleft',title = 'Coverage Rate', legend = c(0,0.5,0.9),col = c('grey',colors),lty = c(2,1,1),lwd = 2, cex = 0.8)

year_round_vacc <- TRUE
output <- Vacc_Sim(parms, 0,0.75,5,15,chis)
total_hosp <- output[[2]]

indices = total_hosp[,1]>52*3 & total_hosp[,1]<11*52
  par(mar = c(2, 2, 1, 1), mgp = c(1.6, 0.5, 0))
  plot(total_hosp[indices,1], total_hosp[indices,2],
       ylim = c(0,1400/TX_pop_size),bty = 'l', type ='l', lwd =2, 
       col ='grey', lty = 2,ylab = '',xlab = '')
  for (i in 1:2){
    lines(total_hosp[indices,1], total_hosp[indices,i+2],
       ylim = c(0,1400/TX_pop_size),bty = 'l', type ='l', lwd =2, 
       col =colors[i])
  }
year_round_vacc <- F
```
# plots for tau = 1.25
```{r}
colors = rev(c('#4D3ECA','#00CEA6'))
chis <- c(0,0.5,0.9)
output <- Vacc_Sim(parms, 0,1.25,5,15,chis)
total_hosp <- output[[2]]


indices = total_hosp[,1]>52*3 & total_hosp[,1]<11*52
  par(mar = c(0.5, 2, 1, 1), mgp = c(1.6, 0.5, 0))
  plot(total_hosp[indices,1], total_hosp[indices,2],
       ylim = c(0,1400/TX_pop_size),bty = 'l', type ='l', lwd =2, 
       col ='grey', lty = 2,ylab = '',xlab = '',xaxt = 'n')
  for (i in 1:2){
    lines(total_hosp[indices,1], total_hosp[indices,i+2],
       ylim = c(0,1400/TX_pop_size),bty = 'l', type ='l', lwd =2, 
       col =colors[i])
  }
  legend('topleft',title = 'Coverage Rate', legend = c(0,0.5,0.9),col = c('grey',colors),lty = c(2,1,1),lwd = 2, cex = 0.8)

year_round_vacc <- TRUE
output <- Vacc_Sim(parms, 0,1.25,5,15,chis)
total_hosp <- output[[2]]

indices = total_hosp[,1]>52*3 & total_hosp[,1]<11*52
  par(mar = c(2, 2, 1, 1), mgp = c(1.6, 0.5, 0))
  plot(total_hosp[indices,1], total_hosp[indices,2],
       ylim = c(0,1400/TX_pop_size),bty = 'l', type ='l', lwd =2, 
       col ='grey', lty = 2,ylab = '',xlab = '')
  for (i in 1:2){
    lines(total_hosp[indices,1], total_hosp[indices,i+2],
       ylim = c(0,1400/TX_pop_size),bty = 'l', type ='l', lwd =2, 
       col =colors[i])
  }
year_round_vacc <- F
```

###### Maternal vs Baby vaccine - CDC timing
```{r}
load("output/TX_parms.RData")
parms <- TX_parms[[4]][1,]
rm(TX_parms)
year_round_vacc = FALSE
# only maternal
output_maternal <- Vacc_Sim(parms, 0,1,5,15,seq(0,1,0.1),mat_vacc = TRUE, baby_vacc = FALSE)
output_baby <- Vacc_Sim(parms, 0,1,5,15,seq(0,1,0.1),mat_vacc = FALSE, baby_vacc = TRUE)
output_both <- Vacc_Sim(parms, 0,1,5,15,seq(0,1,0.1),mat_vacc = TRUE, baby_vacc = TRUE)
output_more_maternal <- Vacc_Sim(parms, 0,1,5,15,seq(0,1,0.1),mat_vacc = TRUE, 
                                 baby_vacc = TRUE, vacc_ratio = 1.5)
output_more_baby <- Vacc_Sim(parms, 0,1,5,15,seq(0,1,0.1),mat_vacc = TRUE, 
                             baby_vacc = TRUE, vacc_ratio = 0.5)
save(output_maternal,file = 'output/CDC_maternal_only.RData')
save(output_baby,file = 'output/CDC_infant_only.RData')
save(output_both,file = 'output/CDC_both.RData')
save(output_more_maternal,file = 'output/CDC_more_maternal_only.RData')
save(output_more_baby,file = 'output/CDC_more_infant_only.RData')
```

```{r}
load('output/CDC_maternal_only.RData')
load('output/CDC_infant_only.RData')
load('output/CDC_both.RData')
load('output/CDC_more_maternal_only.RData')
load('output/CDC_more_infant_only.RData')
names <- c("Only Maternal",  "50% more maternal","Equal Maternal and Baby", "50% more baby" ,"Only Baby")

all_props = NULL
for (i in 1:5){
  output <- list(output_maternal,output_more_maternal,output_both,output_more_baby,output_baby)[[i]]
  prop_coverage <- output[[3]]
  total <- rowSums(prop_coverage)
  new_df <- data.frame(total = total, under1 = prop_coverage[,1])
  colnames(new_df) <- c(paste(names[i], "total"),paste(names[i],"under 1"))
  if (is.null(all_props)) {
    all_props <- new_df
  } else {
    all_props <- cbind(all_props, new_df)
  }
}

CDC_all_props <- all_props[,c(grep("total",colnames(all_props)))]
colnames(CDC_all_props) <- c("1:0","3:2","1:1","2:3","0:1")
tot_max <- max(CDC_all_props)
CDC_all_props <- CDC_all_props/tot_max
CDC_all_props <- as.matrix(CDC_all_props)


CDC_under1_props <- all_props[,c(grep("under 1",colnames(all_props)))]
colnames(CDC_under1_props) <- c("1:0","3:2","1:1","2:3","0:1")
CDC_under1_props <- CDC_under1_props/tot_max
CDC_under1_props <- as.matrix(CDC_under1_props)

# png('figures/supplement/supp6/CDCtotal.png',width = 4.5, height = 3, units = "in", res = 300)
pdf('figures/supplement/supp6/CDCtotal.pdf',width = 4.5, height = 3)
  par(mar = c(2.5, 5, 1, 0.5))
  barplot(CDC_all_props, beside= TRUE, legend = FALSE, 
          col = brewer.pal(nrow(CDC_all_props), "Spectral"),
          main = "",
          xlab = "",
          ylab = "Total Standardized\n Hospitalizations")
dev.off()

# png('figures/supplement/supp6/CDCunder1.png',width = 4.5, height = 3, units = "in", res = 300)
pdf('figures/supplement/supp6/CDCunder1.pdf',width = 4.5, height = 3)
  par(mar = c(2.5, 5, 1, 0.5))
  barplot(CDC_under1_props, beside= TRUE, legend = FALSE, 
          col = brewer.pal(nrow(CDC_under1_props), "Spectral"),
          main = "",
          xlab = "",
          ylab = "Under 1 Standardized\n Hospitalizations",
          ylim = c(0,1))
dev.off()
 
# png('figures/supplement/supp6/legend.png',width = 1.0, height = 3.5, units = "in", res = 300)
pdf('figures/supplement/supp6/legend.pdf',width = 1.0, height = 3.5)
par(mar = c(0.5, 0.0, 0.0, 0.0))
plot.new()

legend("center", legend = seq(0, 1, 0.1),
       fill = brewer.pal(nrow(CDC_all_props), "Spectral"),
       cex = 1, bg = "white",bty = "n")
dev.off()
```
```{r}
CDC_all_props_red <- 1 - CDC_all_props[11,]/CDC_all_props[1,]
CDC_under1_props_red <- 1 - CDC_under1_props[11,]/CDC_under1_props[1,]
print('All')
print(CDC_all_props_red)
print('Under 1')
print(CDC_under1_props_red)
```

###### Maternal vs Baby vaccine- year round vaccination
```{r}
load("output/TX_parms.RData")
parms <- TX_parms[[4]][1,]
rm(TX_parms)
year_round_vacc = TRUE
# only maternal
output_maternal <- Vacc_Sim(parms, 0,1,5,15,seq(0,1,0.1),mat_vacc = TRUE, baby_vacc = FALSE)
output_baby <- Vacc_Sim(parms, 0,1,5,15,seq(0,1,0.1),mat_vacc = FALSE, baby_vacc = TRUE)
output_both <- Vacc_Sim(parms, 0,1,5,15,seq(0,1,0.1),mat_vacc = TRUE, baby_vacc = TRUE)
output_more_maternal <- Vacc_Sim(parms, 0,1,5,15,seq(0,1,0.1),mat_vacc = TRUE, 
                                 baby_vacc = TRUE, vacc_ratio = 1.5)
output_more_baby <- Vacc_Sim(parms, 0,1,5,15,seq(0,1,0.1),mat_vacc = TRUE, 
                             baby_vacc = TRUE, vacc_ratio = 0.5)
save(output_maternal,file = 'output/yearround_maternal_only.RData')
save(output_baby,file = 'output/yearround_infant_only.RData')
save(output_both,file = 'output/yearround_both.RData')
save(output_more_maternal,file = 'output/yearround_more_maternal_only.RData')
save(output_more_baby,file = 'output/yearround_more_infant_only.RData')
```


```{r}
load('output/yearround_maternal_only.RData')
load('output/yearround_infant_only.RData')
load('output/yearround_both.RData')
load('output/yearround_more_maternal_only.RData')
load('output/yearround_more_infant_only.RData')
names <- c("Only Maternal",  "50% more maternal","Equal Maternal and Baby", "50% more baby" ,"Only Baby")

all_props = NULL
for (i in 1:5){
  output <- list(output_maternal,output_more_maternal,output_both,output_more_baby,output_baby)[[i]]
  prop_coverage <- output[[3]]
  total <- rowSums(prop_coverage)
  new_df <- data.frame(total = total, under1 = prop_coverage[,1])
  colnames(new_df) <- c(paste(names[i], "total"),paste(names[i],"under 1"))
  if (is.null(all_props)) {
    all_props <- new_df
  } else {
    all_props <- cbind(all_props, new_df)
  }
}

YearRound_all_props <- all_props[,c(grep("total",colnames(all_props)))]
colnames(YearRound_all_props) <- c("1:0","3:2","1:1","2:3","0:1")
tot_max <- max(YearRound_all_props)
YearRound_all_props <- YearRound_all_props/tot_max
YearRound_all_props <- as.matrix(YearRound_all_props)


YearRound_under1_props <- all_props[,c(grep("under 1",colnames(all_props)))]
colnames(YearRound_under1_props) <- c("1:0","3:2","1:1","2:3","0:1")
YearRound_under1_props <- YearRound_under1_props/tot_max
YearRound_under1_props <- as.matrix(YearRound_under1_props)

png('figures/supplement/supp6/YearRoundtotal.png',width = 4.5, height = 3, units = "in", res = 300)
# pdf('figures/supplement/supp6/YearRoundtotal.pdf',width = 4.5, height = 3)
  par(mar = c(2.5, 5, 1, 0.5))
  barplot(YearRound_all_props, beside= TRUE, legend = FALSE, 
          col = brewer.pal(nrow(YearRound_all_props), "Spectral"),
          main = "",
          xlab = "",
          ylab = "Total Standardized\n Hospitalizations")
dev.off()

png('figures/supplement/supp6/YearRoundunder1.png',width = 4.5, height = 3, units = "in", res = 300)
# pdf('figures/supplement/supp6/YearRoundunder1.pdf',width = 4.5, height = 3)
  par(mar = c(2.5, 5, 1, 0.5))
  barplot(YearRound_under1_props, beside= TRUE, legend = FALSE, 
          col = brewer.pal(nrow(YearRound_under1_props), "Spectral"),
          main = "",
          xlab = "",
          ylab = "Under 1 Standardized\n Hospitalizations",
          ylim = c(0,1))
dev.off()
 
```


```{r}
YearRound_all_props_red <- 1 - YearRound_all_props[11,]/YearRound_all_props[1,]
YearRound_under1_props_red <- 1 - YearRound_under1_props[11,]/YearRound_under1_props[1,]
print('All')
print(YearRound_all_props_red)
print('Under 1')
print(YearRound_under1_props_red)
```

## heatmaps
```{r,eval=FALSE}
load("output/TX_parms.RData")
parms <- TX_parms[[4]][1,]
rm(TX_parms)
coverage = seq(0,1,0.05)
shifts <- seq(0,15,1)
year_round_vacc = FALSE

rm(stable_peaks)
stable_peaks <- matrix(NA,nrow = length(coverage), ncol = length(shifts))
colnames(stable_peaks) = shifts
rownames(stable_peaks) = coverage

for (i in 1:length(shifts)){
  print(shifts[i])
  for (j in 1:length(coverage)){
    parms$vacc_shift = shifts[i]
    output <- Vacc_Sim(parms, 0,0.75,5,15,coverage[j])
    max_peak <- output[[4]]
    mat <- max_peak[[1]]
    stable_peaks[j,i] <- as.numeric(mat[nrow(mat),2])
  }
}

save(stable_peaks,file = 'output/heatmap_stablepeaks_covweeks_rural.RData')

rm(stable_peaks)
stable_peaks <- matrix(NA,nrow = length(coverage), ncol = length(shifts))
colnames(stable_peaks) = shifts
rownames(stable_peaks) = coverage

for (i in 1:length(shifts)){
  print(shifts[i])
  for (j in 1:length(coverage)){
    parms$vacc_shift = shifts[i]
    output <- Vacc_Sim(parms, 0,1.25,5,15,coverage[j])
    max_peak <- output[[4]]
    mat <- max_peak[[1]]
    stable_peaks[j,i] <- as.numeric(mat[nrow(mat),2])
  }
}
save(stable_peaks,file = 'output/heatmap_stablepeaks_covweeks_urban.RData')
```

```{r}
maternal_weeks <- seq(22,52, by =2)
infant_weeks <- c(seq(26,52, by =2),rep(52,2))
coverage = seq(0,1,0.05)
shifts <- seq(0,15,0.5)

color_choice <- rev(parula(100))

load('output/heatmap_stablepeaks_covweeks_rural.RData')
stable_peaks <- stable_peaks/stable_peaks[1,1]
par(mar = c(1.5, 1.5, 1.5, 0.5),mgp = c(1.6, 1, 0))
image(t(stable_peaks),
        xlab = '',
        ylab = '',
        col=color_choice,
        axes = F,
        zlim=c(0.1,1))
axis(2,at=seq(0,1, length=length(coverage)), labels = coverage,tick = F,line = -0.7)
axis(1,at=seq(0,1, length=length(infant_weeks)), labels = infant_weeks,tick = F,line = -0.7)
axis(3,at=seq(0,1, length=length(maternal_weeks)), labels = maternal_weeks,tick = F,line = -0.7)

load('output/heatmap_stablepeaks_covweeks_urban.RData')
stable_peaks <- stable_peaks/stable_peaks[1,1]

par(mar = c(1.5, 1.5, 1.5, 2),mgp = c(1.6, 1, 0))
image.plot(t(stable_peaks),
        xlab = '',
        ylab = '',
        col=color_choice,
        legend.lab="",
        axes = F,
        legend.line = 2.3,zlim= c(0.1,1))
axis(2,at=seq(0,1, length=length(coverage)), labels = coverage,tick = F,line = -0.7)
axis(1,at=seq(0,1, length=length(infant_weeks)), labels = infant_weeks,tick = F,line = -0.7)
axis(3,at=seq(0,1, length=length(maternal_weeks)), labels = maternal_weeks,tick = F,line = -0.7)

```


```{r}
load("output/TX_parms.RData")
parms <- TX_parms[[4]][1,]
rm(TX_parms)
coverage = seq(0,1,0.05)
shifts <- seq(0,15,1)
year_round_vacc = FALSE
# -13  is no vaccine of either. 
rm(reduction)
rm(max_peak)
rm(time_shifts)
max_peak <- matrix(NA,nrow = length(coverage), ncol = length(shifts))
colnames(max_peak) = shifts
rownames(max_peak) = coverage
reduction <- matrix(NA,nrow = length(coverage), ncol = length(shifts))
colnames(reduction) = shifts
rownames(reduction) = coverage
time_shifts <- matrix(NA,nrow = length(coverage), ncol = length(shifts))
colnames(time_shifts) = shifts
rownames(time_shifts) = coverage


coverage <- c(0.5)
shifts <- seq(5,15,1)
for (i in 1:length(shifts)){
  print(shifts[i])
  for (j in 1:length(coverage)){
    parms$vacc_shift = shifts[i]
    output <- Vacc_Sim(parms, 0,1.25,5,10,coverage[j])
    under1 <- output[[1]]
  
    last_year_index <- under1[,1]>(max(under1[,1])-(365.25/7))
    last_year_hosps <- under1[last_year_index,]
    max_index <- which.max(last_year_hosps[,2])
    
    indices = under1[,1]>(365.25/7*6+90.25/7+3)
    if (i ==1 && j == 1){
      no_vacc <- sum(under1[indices,2])
      under1_max <- max(under1[indices,2])
      rel_time <- last_year_hosps[max_index,1]
    }
    max_peak[j,i] <-max(under1[indices,2])/under1_max
    reduction[j,i] <- sum(under1[indices,2])
    time_shifts[j,i] <- (last_year_hosps[max_index,1] -rel_time)
  }
}

save(max_peak,file = 'output/heatmap_maxpeak_covweeks_urban.RData')
save(reduction,file = 'output/heatmap_reduction_covweeks_urban.RData')
save(time_shifts,file = 'output/heatmap_timeshifts_covweeks_urban.RData')
```

```{r}
source('source/SIR.R')
source('source/Vacc_Sim.R')
load("output/TX_parms.RData")
parms <- TX_parms[[4]][1,]
rm(TX_parms)
coverage = seq(0,1,0.05)
shifts <- seq(0,15,1)
year_round_vacc = FALSE
# -13  is no vaccine of either. 
rm(reduction)
rm(max_peak)
rm(time_shifts)
max_peak <- matrix(NA,nrow = length(coverage), ncol = length(shifts))
colnames(max_peak) = shifts
rownames(max_peak) = coverage
reduction <- matrix(NA,nrow = length(coverage), ncol = length(shifts))
colnames(reduction) = shifts
rownames(reduction) = coverage
time_shifts <- matrix(NA,nrow = length(coverage), ncol = length(shifts))
colnames(time_shifts) = shifts
rownames(time_shifts) = coverage
for (i in 1:length(shifts)){
  print(shifts[i])
  for (j in 1:length(coverage)){
    parms$vacc_shift = shifts[i]
    output <- Vacc_Sim(parms, 0,0.75,5,10,coverage[j])
    under1 <- output[[1]]
  
    last_year_index <- under1[,1]>(max(under1[,1])-(365.25/7))
    last_year_hosps <- under1[last_year_index,]
    max_index <- which.max(last_year_hosps[,2])
    
    indices = under1[,1]>(365.25/7*6+90.25/7+3)
    if (i ==1 && j == 1){
      no_vacc <- sum(under1[indices,2])
      under1_max <- max(under1[indices,2])
      rel_time <- last_year_hosps[max_index,1]
    }
    max_peak[j,i] <-max(under1[indices,2])/under1_max
    reduction[j,i] <- sum(under1[indices,2])
    time_shifts[j,i] <- (last_year_hosps[max_index,1] -rel_time)
  }
}

save(max_peak,file = 'output/heatmap_maxpeak_covweeks_rural.RData')
save(reduction,file = 'output/heatmap_reduction_covweeks_rural.RData')
save(time_shifts,file = 'output/heatmap_timeshifts_covweeks_rural.RData')
```




```{r}

load('output/heatmap_maxpeak_covweeks_urban.RData')
peak_min <- min(max_peak)/max_peak[1,1]
peak_max <- max(max_peak)/max_peak[1,1]
load('output/heatmap_maxpeak_covweeks_rural.RData')
if (max(max_peak)/max_peak[1,1]>peak_max){
  peak_max <-max(max_peak)/max_peak[1,1]
}
if (min(max_peak)/max_peak[1,1]<peak_min){
  peak_min <- min(max_peak)/max_peak[1,1]
}
```


```{r}
# CDC infant is 26 weeks
# CDC maternal is 21.8 weeks
maternal_weeks <- seq(22,52, by =2)
infant_weeks <- c(seq(26,52, by =2),rep(52,2))
coverage = seq(0,1,0.05)
shifts <- seq(0,15,0.5)

color_choice <- rev(parula(100))
load('output/heatmap_reduction_covweeks_urban.RData') #reduction

reduction <- reduction/reduction[1,1]

# reduction
par(mar = c(1.5, 1.5, 1.5, 2),mgp = c(1.6, 1, 0))
image.plot(t(reduction),
        xlab = '',
        ylab = '',
        col=color_choice,
        legend.lab="",
        axes = F,
        legend.line = 2.3,zlim= c(0.15,1))
axis(2,at=seq(0,1, length=length(coverage)), labels = coverage,tick = F,line = -0.7)
axis(1,at=seq(0,1, length=length(infant_weeks)), labels = infant_weeks,tick = F,line = -0.7)
axis(3,at=seq(0,1, length=length(maternal_weeks)), labels = maternal_weeks,tick = F,line = -0.7)


# max_peak
load('output/heatmap_maxpeak_covweeks_urban.RData')
max_peak<- max_peak/max_peak[1,1]
par(mar = c(1.5, 1.5, 1.5, 2), mgp = c(1.6, 1, 0))
image.plot(t(max_peak),
        xlab = '',
        ylab = '',
        col=color_choice,
        legend.lab="",
        axes = F,
        legend.line = 2.3,zlim = c(peak_min,peak_max))
axis(2,at=seq(0,1, length=length(coverage)), labels = coverage,tick = F,line = -0.7)
axis(1,at=seq(0,1, length=length(infant_weeks)), labels = infant_weeks,tick = F,line = -0.7)
axis(3,at=seq(0,1, length=length(maternal_weeks)), labels = maternal_weeks,tick = F,line = -0.7)


load('output/heatmap_timeshifts_covweeks_urban.RData')
time_shifts <- time_shifts%% (365.25/7)
par(mar = c(1.5, 1.5, 1.5, 2), mgp = c(1.6, 1, 0))
image.plot(t(time_shifts),
        xlab = '',
        ylab = '',
        col=color_choice,
        legend.lab="",
        axes = F,
        legend.line = 2.3,zlim = c(-0.5,33))
axis(2,at=seq(0,1, length=length(coverage)), labels = coverage,tick = F,line = -0.7)
axis(1,at=seq(0,1, length=length(infant_weeks)), labels = infant_weeks,tick = F,line = -0.7)
axis(3,at=seq(0,1, length=length(maternal_weeks)), labels = maternal_weeks,tick = F,line = -0.7)

```

```{r}
# CDC infant is 26 weeks
# CDC maternal is 21.8 weeks
maternal_weeks <- seq(22,52, by =2)
infant_weeks <- c(seq(26,52, by =2),rep(52,2))
coverage = seq(0,1,0.05)
shifts <- seq(0,15,0.5)
library(pals)
library(fields)
color_choice <- rev(parula(100))
load('output/heatmap_reduction_covweeks_rural.RData')
#reduction
reduction <- reduction/reduction[1,1]
par(mar = c(1.5, 1.5, 1.5, 0.5),mgp = c(1.6, 1, 0))
image(t(reduction),
        xlab = '',
        ylab = '',
        col=color_choice,
        # legend.lab="Reduction in Under 1 Hospitalizations",
        axes = F,
        zlim=c(0.15,1))
axis(2,at=seq(0,1, length=length(coverage)), labels = coverage,tick = F,line = -0.7)
axis(1,at=seq(0,1, length=length(infant_weeks)), labels = infant_weeks,tick = F,line = -0.7)
axis(3,at=seq(0,1, length=length(maternal_weeks)), labels = maternal_weeks,tick = F,line = -0.7)

# max_peak
load('output/heatmap_maxpeak_covweeks_rural.RData')
max_peak<- max_peak/max_peak[1,1]
par(mar = c(1.5, 1.5, 1.5, 0.5),mgp = c(1.6, 1, 0))
image(t(max_peak),
        xlab = '',
        ylab = '',
        col=color_choice,
        # legend.lab="Max Peak (Rel. to No Vacc.)",
        axes = F,
        legend.line = 2.3,zlim =c(peak_min,peak_max))
axis(2,at=seq(0,1, length=length(coverage)), labels = coverage,tick = F,line = -0.7)
axis(1,at=seq(0,1, length=length(infant_weeks)), labels = infant_weeks,tick = F,line = -0.7)
axis(3,at=seq(0,1, length=length(maternal_weeks)), labels = maternal_weeks,tick = F,line = -0.7)
dev.off()

load('output/heatmap_timeshifts_covweeks_rural.RData')
par(mar = c(1.5, 1.5, 1.5, 0.5),mgp = c(1.6, 1, 0))
image(t(time_shifts),
        xlab = '',
        ylab = '',
        col=color_choice,
        # legend.lab="Max Peak (Rel. to No Vacc.)",
        legend.line = 2.3,axes = F,zlim = c(-0.5,33))
axis(2,at=seq(0,1, length=length(coverage)), labels = coverage,tick = F,line = -0.7)
axis(1,at=seq(0,1, length=length(infant_weeks)), labels = infant_weeks,tick = F,line = -0.7)
axis(3,at=seq(0,1, length=length(maternal_weeks)), labels = maternal_weeks,tick = F,line = -0.7)

```



## Step funciton

```{r}
# only want one set of parameters for now, so delete all others
load("output/TX_parms.RData")
parms <- TX_parms[[4]][1,]
rm(TX_parms)

colors = rev(c('#4D3ECA','#00CEA6'))
chis <- c(0,0.5,0.9)
parms$step_function <- TRUE
parms$vacc_shift <- 0
output <- Vacc_Sim(parms, 0,1,5,15,chis)
total_hosp <- output[[2]]

indices = total_hosp[,1]>52*3 & total_hosp[,1]<11*52
  par(mar = c(0.5, 2, 1, 1), mgp = c(1.6, 0.5, 0))
  plot(total_hosp[indices,1], total_hosp[indices,2]*TX_pop_size,
       ylim = c(0,1700),bty = 'l', type ='l', lwd =2, 
       col ='grey', lty = 2,ylab = '',xlab = '',xaxt = 'n')
  for (i in 1:2){
    lines(total_hosp[indices,1], total_hosp[indices,i+2]*TX_pop_size,
       ylim = c(0,1700),bty = 'l', type ='l', lwd =2, 
       col =colors[i])
  }
  legend('topleft',title = 'Coverage Rate', legend = c(0,0.5,0.9),col = c('grey',colors),lty = c(2,1,1),lwd = 2, cex = 0.8)
  
## new
  
chis <- c(0,0.5,0.9)
parms$step_function <- TRUE
parms$vacc_shift <- 16
output <- Vacc_Sim(parms, 0,1,5,15,chis)
total_hosp <- output[[2]]


indices = total_hosp[,1]>52*3 & total_hosp[,1]<11*52
  par(mar = c(0.5, 2, 1, 1), mgp = c(1.6, 0.5, 0))
  plot(total_hosp[indices,1], total_hosp[indices,2]*TX_pop_size,
       ylim = c(0,1400),bty = 'l', type ='l', lwd =2, 
       col ='grey', lty = 2,ylab = '',xlab = '',xaxt = 'n')
  for (i in 1:2){
    lines(total_hosp[indices,1], total_hosp[indices,i+2]*TX_pop_size,
       ylim = c(0,1400),bty = 'l', type ='l', lwd =2, 
       col =colors[i])
  }
  legend('topleft',title = 'Coverage Rate', legend = c(0,0.5,0.9),col = c('grey',colors),lty = c(2,1,1),lwd = 2, cex = 0.8)
  
  
  

year_round_vacc <- TRUE
output <- Vacc_Sim(parms, 0,1,5,15,chis)
total_hosp <- output[[2]]

indices = total_hosp[,1]>52*3 & total_hosp[,1]<11*52
  par(mar = c(2, 2, 1, 1), mgp = c(1.6, 0.5, 0))
  plot(total_hosp[indices,1], total_hosp[indices,2]*TX_pop_size,
       ylim = c(0,1700),bty = 'l', type ='l', lwd =2, 
       col ='grey', lty = 2,ylab = '',xlab = '')
  for (i in 1:2){
    lines(total_hosp[indices,1], total_hosp[indices,i+2]*TX_pop_size,
       ylim = c(0,1700),bty = 'l', type ='l', lwd =2, 
       col =colors[i])
  }
year_round_vacc <- F
```
