---
title: "Bifurcations"
author: "Presley Kimball"
date: "2024-06-27"
output: html_document
---

## Set up

```{r}
library(readxl)
library(pals)
library(tidyverse)
library(dplyr)
library(deSolve)
library(RColorBrewer)
library(ggplot2)
library(viridis)
library(lhs)

# set your working directory to be the overall file folder
setwd("C:/Users/prkimbal/Summer2024/AgeStructuredRSVModelWithUrbanization")

# set color palettes
palette_4 <- brewer.pal(4, "Spectral") 
palette_5 <- brewer.pal(5, "Spectral") 
palette_6 <- brewer.pal(6, "Spectral") 
```
## Bringing in Texas Data
```{r}
# load in Texas data
load("/data/TexasData/TX_pop_size.RData")
load("/data/TexasData/TX_age_cat.RData")
load("/data/TexasData/TX_sum.RData")

# # load rural data
# load("/data/TexasData/TX_rural_pop_size.RData")
# load("/data/TexasData/TX_rural_age_cat.RData")
# load("/data/TexasData/TX_rural_sum.RData")
# 
# # load urban data
# load("/data/TexasData/TX_urban_pop_size.RData")
# load("/data/TexasData/TX_urban_age_cat.RData")
# load("/data/TexasData/TX_urban_sum.RData")
```

## Load in contact matrix and correct the format
```{r}
# Call in contact matrix
K <- read_excel("/data/US_contact.xlsx")
K <- as.matrix(K)
# duplicate the first column (match other age groups)
K <- cbind(K[,1],K[,1],K[,1],K[,1],K)
K <- rbind(K[1,],K[1,],K[1,],K[1,],K)
colnames(K) <- c("0-1","1-2","2-3","3-4","4-5","5-10", "10-15", "15-20", "20-25",
                 "25-30", "30-35", "35-40", "40-45", "45-50", "50-55", "55-60",
                 "60-65", "65-70", "70-75", "75+")
rownames(K) <- c("0-1","1-2","2-3","3-4","4-5","5-10", "10-15", "15-20", "20-25",
                 "25-30", "30-35", "35-40", "40-45", "45-50", "50-55", "55-60",
                 "60-65", "65-70", "70-75", "75+")

# transpose the matrix to match interpretation of main manuscript
K <- t(K)

# View contact matrix
heatmap(K, Rowv=NA, Colv=NA, scale='none')
```

## Initializing age groups
We will use the general age distribution of the US census in 2010.
\url{https://www.census.gov/content/dam/Census/library/publications/2011/dec/c2010br-03.pdf}
```{r}
N0_ages <- c("0-1"= 20201362/5,
            "1-2" = 20201362/5,
            "2-3" = 20201362/5,
            "3-4" = 20201362/5,
            "4-5" = 20201362/5,
            "5-10" = 20348657,
            "10-15" = 20677194,
            "15-20" = 22040343,
            "20-25" = 21585999,
            "25-30" = 21101849,
            "30-35" = 19962099,
            "35-40" = 20179642,
            "40-45" = 20890964,
            "45-50" = 22708591,
            "50-55" = 22298125,
            "55-60" = 19664805,
            "60-65" = 16817924,
            "65-70" = 12435263,
            "70-75" = 9278166,
            "75+" = 7317795+5743327+3620459+1448366+371244+53364)

```

## Setting Global Parameters
```{r}
# Set global variables. Note all rates are by week
Lambda = c("0-1"=(385746/25145561)/365.25*7,"1-2" = 0,"2-3" = 0,"3-4" = 0,"4-5" = 0,
           "5-10" = 0,"10-15" = 0,"15-20" = 0,"20-25" = 0,"25-30" = 0,"30-35" = 0,
           "35-40" = 0,"40-45" = 0,"45-50" = 0,"50-55" = 0,"55-60" = 0,"60-65" = 0,
           "65-70" = 0,"70-75" = 0,"75+" = 0)
mu = (385746/25145561)/365.25*7
ages <- c(0:4,seq(5,75,by=5))
T <- length(ages)
age_cats <- c("0-1","1-2","2-3","3-4","4-5","5-10", "10-15", "15-20", "20-25",
              "25-30", "30-35", "35-40", "40-45", "45-50", "50-55", "55-60",
              "60-65", "65-70", "70-75", "75+")
m = 1/200*7
gamma_vec = c(1/10,1/7,1/5,1/5)*7
r_vec = c(1/(diff(ages)*365.25),0)*7
rho_vec = c(1,0.75,0.51,0.51)
sigma_vec = c(1,0.76,0.6,0.4)
p_R = 1
K = K
h_1 = c((0.2*0.44*0.9/4+0.08*0.43*0.9/4+0.07*0.23*0.9/4+0.06*0.22*0.9/4*2),# 0-1
        0.06*0.21*0.8,# 1-2
        0.05*0.2*0.8,# 2-3
        0.05*0.2*0.8,#3-4
        0.05*0.2*0.8,#4-5
        0.05*0.2*0.8,#5-10
        rep(0.02*0.05,length(ages)-6)# above 5
        )
h_2 = 0.4*h_1
h_3 = rep(0,length(ages))# set to zero, maybe close to 0 would be better
nu_m <- (1/6)*(12*7/365.25)
nu_b <- (1/5)*(12*7/365.25)
iota_m <- 1-0.57
iota_b <- 1-0.8
```

## General setup
```{r}
StateNames <- c('S0','S1','S2','S3','I1','I2','I3','I4','R','Vm','Vb')
States <- array(NA, dim=c(length(ages), length(StateNames) )) 
dimnames(States)[[1]] <- age_cats
dimnames(States)[[2]] <- StateNames

States_IC <- States

States_IC[,c('S1','S2','S3','I2','I3','I4','R','Vm','Vb')]  = 0
States_IC[,'S0'] = c(N0_ages[1:nrow(States_IC)])
States_IC[,'I1'] = c(rep(10000,nrow(States_IC)))  #initializes with 10000 infected person per age group (This is since the N0_ages values are based on entire US population. We rescale down to population being simulated later. This allows for base endemic to occur.)

# Scale total population size down to 1 (so that the population size is stable)
# We are assuming that all locations have similar population distribution and 
# thus are rescaled by the population in each location (done later)
States_IC <- States_IC/sum(States_IC)

# convert initial condition to a vector for ODE solver
States_IC_vec <- as.vector(States_IC)
names(States_IC_vec) <- paste(rep(rownames(States_IC),ncol(States_IC)),
                              rep(colnames(States_IC),each = nrow(States_IC)), sep = " ")
```
## Tau vector function
Function that calculates the tau vector based on two inputs:
$$\tau = \tau_1*(\text{age_midpoints})+\tau_2$$ only for first five age_categories
```{r}
tau_vec <- function(tau_1,tau_2){
  tau <- rep(1,length(age_cats))
  for(i in 1:5){
    tau[i] <- tau_1 * ((i-1)+0.5)+tau_2
  }
  return(tau)
}
```




## SIR model
```{r}
source('source/SIR.R')
```

## Tracking hospitalizations

```{r}
source('source/Track_Hospitalizations.R')
```

## ODE solver of the model
```{r}
ODE_solve_SIR <- function(parms,States_IC_vec,burn_pd_yrs,lngth_soln_months){
  times <- seq(0,(ceiling(365.25/7*burn_pd_yrs)+lngth_soln_months),by = 1)
  solution <- ode(y=States_IC_vec, t=times,func=SIR, method = "ode45",
                  parms=parms)
  final_soln <- solution[(nrow(solution)-lngth_soln_months+1):nrow(solution),]
  # Reset time-scale to match the timescale of the data
  final_soln[,"time"] <- final_soln[,"time"]- min(final_soln[,"time"])
  return(final_soln)
}
```

```{r,eval=FALSE}
load("output/TX_parms.RData")

parms <- TX_parms[[4]][1,]
parms$chi_b <- 0
parms$chi_m <- 0
burn_pd <- 20
  
  parms$tau_1 <- 0
  parms$tau_2 <- 1
  parms$alpha_1 <- 0.3
  parms$alpha_2 <- 0.1
  
  
  # get solution using given parameters
  solution <- ODE_solve_SIR(parms,States_IC_vec,burn_pd,522)
  
  
  #### SHANNON'S ENTROPY INTENSITY CALCULATION ####
  # get only infected data from the solution
  I_indices <- grep("I",colnames(solution))
  Infected <- rowSums(solution[,I_indices] )
  
  pdf_avg <- rep(NA, 52)
  indices <- (0:9)*52
  for (i in 1:52){
    pdf_avg[i] <- mean(Infected[indices+i])
  }
  pdf_avg <- pdf_avg/sum(pdf_avg)
  pdf_avg <- pdf_avg[pdf_avg != 0]
  Intensity <- 1- (1*sum(pdf_avg*log(pdf_avg)))/(52*sum(1/52*log(1/52)))
  print(Intensity)
```



## Bifucation function
```{r}
Bifurcation_outputs <- function(parms,tau_1,tau_2,alpha_1,alpha_2){
  burn_pd <- 20
  
  parms$tau_1 <- tau_1
  parms$tau_2 <- tau_2
  parms$alpha_1 <- alpha_1
  parms$alpha_2 <- alpha_2
  
  
  # get solution using given parameters
  solution <- ODE_solve_SIR(parms,States_IC_vec,burn_pd,522)
  
  
  #### SHANNON'S ENTROPY INTENSITY CALCULATION ####
  # get only infected data from the solution
  I_indices <- grep("I",colnames(solution))
  Infected <- rowSums(solution[,I_indices] )
  
  pdf_avg <- rep(NA, 52)
  indices <- (0:9)*52
  for (i in 1:52){
    pdf_avg[i] <- mean(Infected[indices+i])
  }
  pdf_avg <- pdf_avg/sum(pdf_avg)
  pdf_avg <- pdf_avg[pdf_avg != 0]
  Intensity <- 1- (1*sum(pdf_avg*log(pdf_avg)))/(52*sum(1/52*log(1/52)))
  
 #### PERIODICITY CALCULATION ####
  Infected <- as.data.frame(Infected)
  Infected$time <- 1:522
  
  maxes <- numeric(10)
  for(i in 1:10){
    times <- 1:52+(i-1)*52
    current_infected <- Infected[times,]
    maxes[i] <- max(current_infected$Infected)
  }
  rounded_maxes <- round(maxes,4)
  
  Unique_maxes <- unique(rounded_maxes)
  if(max(Unique_maxes)>0){
    ratio <- min(Unique_maxes)/max(Unique_maxes)
    if(ratio >= (1/1.1)){
      periodicity_10 <- 1
    } else{
      max_median <- median(rounded_maxes)
      below_median <- rounded_maxes[rounded_maxes<= max_median]
      above_median <- rounded_maxes[rounded_maxes>= max_median]
      if(max(below_median)==0){
        below_10 = TRUE
      } else {
        ratio <- min(below_median)/max(below_median)
        below_10 = (ratio >= 1/1.1)
      }
      if(min(above_median)==0){
        above_10 = FALSE
      } else {
        ratio <- min(above_median)/max(above_median)
        above_10 = (ratio >= 1/1.1)
      }
      if(below_10 == TRUE & above_10 == TRUE){
        periodicity_10 <- 2
      } else {
        periodicity_10 <- length(Unique_maxes)
      }
    }
    ratio <- min(Unique_maxes)/max(Unique_maxes)
    if(ratio >= (1/1.05)){
      periodicity_05 <- 1
    } else{
      max_median <- median(rounded_maxes)
      below_median <- rounded_maxes[rounded_maxes<= max_median]
      above_median <- rounded_maxes[rounded_maxes>= max_median]
      if(max(below_median)==0){
        below_05 = TRUE
      } else {
        ratio <- min(below_median)/max(below_median)
        below_05 = (ratio >= 1/1.05)
      }
      if(min(above_median)==0){
        above_05 = FALSE
      } else {
        ratio <- min(above_median)/max(above_median)
        above_05 = (ratio >= 1/1.05)
      }
      if(below_05 == TRUE & above_05 == TRUE){
        periodicity_05 <- 2
      } else {
        periodicity_05 <- length(Unique_maxes)
      }
    }
    ratio <- min(Unique_maxes)/max(Unique_maxes)
    if(ratio >= (1/1.025)){
      periodicity_025 <- 1
    } else{
      max_median <- median(rounded_maxes)
      below_median <- rounded_maxes[rounded_maxes<= max_median]
      above_median <- rounded_maxes[rounded_maxes>= max_median]
      if(max(below_median)==0){
        below_025 = TRUE
      } else {
        ratio <- min(below_median)/max(below_median)
        below_025 = (ratio >= 1/1.025)
      }
      if(min(above_median)==0){
        above_025 = FALSE
      } else {
        ratio <- min(above_median)/max(above_median)
        above_025 = (ratio >= 1/1.025)
      }
      if(below_025 == TRUE & above_025 == TRUE){
        periodicity_025 <- 2
      } else {
        periodicity_025 <- length(Unique_maxes)
      }
    }
  } else {
    periodicity_10 <- 0
    periodicity_05 <- 0
    periodicity_025 <- 0
  }
  
  #### prop0_1 calculation ####
  All_infected <- solution[,I_indices]
  infected_prop <- numeric(length(age_cats))
  for(i in 1:length(age_cats)){
    current_infected <- All_infected[,grep(paste(age_cats[i]," ",sep=""),
                                           colnames(All_infected))]
    infected_prop[i] <- sum(current_infected)
  }
  
  infected_prop <- infected_prop/sum(infected_prop)
  
  prop0_1 <- infected_prop[1]
  
  
  #### AVG SEASONALITY LENGTH CALCULATION ####
  max_times <- numeric(10)
  for(i in 1:10){
    times <- 1:52+(i-1)*52
    current_infected <- Infected[times,]
    current_infected <- current_infected[order(current_infected$Infected,
                                               decreasing = TRUE),]
    max_times[i] <- current_infected$time[1]
  }
  
  avg_szn <- mean(diff(max_times))
  
  results <- list(Intensity,periodicity_10,periodicity_05,periodicity_025,prop0_1,avg_szn)
  return(results)
}
```


```{r}
load("output/TX_parms.RData")

Texas_best_parms <- TX_parms[[4]][1,]
Texas_best_parms$chi_b <- 0
Texas_best_parms$chi_m <- 0
trial <- Bifurcation_outputs(Texas_best_parms,0,1.25,0.35,0.04)
```


want to make for alpha_1 and alpha_2, alpha_2 and tau_2 (tau_1 = 0)
```{r}
alpha_1 <- seq(round(Texas_best_parms$alpha_1,3)-0.3,
               round(Texas_best_parms$alpha_1,3)+0.3,0.005)
alpha_2 <- seq(round(Texas_best_parms$alpha_2,4)-0.1,
               round(Texas_best_parms$alpha_2,4)+0.1,0.002)
tau_2 <- seq(0.65,1.35,0.005)
parm_set <- expand.grid(alpha_1= alpha_1,alpha_2= alpha_2)
parm_set$tau_2 <- 1
add_parm_set <- expand.grid(alpha_2= alpha_2,tau_2 = tau_2)
add_parm_set$alpha_1 <- Texas_best_parms$alpha_1
add2_parm_set <- expand.grid(alpha_1 = alpha_1, tau_2 = tau_2)
add2_parm_set$alpha_2 <- Texas_best_parms$alpha_2
parm_set <- rbind(add_parm_set,add2_parm_set)


# fix all other values.
parm_set$alpha_3 <- Texas_best_parms$alpha_3
parm_set$q_1 <- Texas_best_parms$q_1
parm_set$q_2 <- Texas_best_parms$q_2
parm_set$q_3 <- Texas_best_parms$q_3
parm_set$q_4 <- Texas_best_parms$q_4
parm_set$q_5 <- Texas_best_parms$q_5
parm_set$q_6 <- Texas_best_parms$q_6
parm_set$chi_m <- 0
parm_set$chi_b <- 0

parm_set$Intensity <- NA
parm_set$periodicity_10 <- NA
parm_set$periodicity_05 <- NA
parm_set$periodicity_025 <- NA
parm_set$prop0_1 <- NA
parm_set$avg_szn <- NA
```

```{r}
start = 1
for(i in  start:nrow(parm_set)){
  output <- Bifurcation_outputs(Texas_best_parms,0,parm_set$tau_2[i],parm_set$alpha_1[i],parm_set$alpha_2[i])
  parm_set$Intensity[i] <- output[[1]]
  parm_set$periodicity_10[i] <- output[[2]]
  parm_set$periodicity_05[i] <- output[[3]]
  parm_set$periodicity_025[i] <- output[[4]]
  parm_set$prop0_1[i] <- output[[5]]
  parm_set$avg_szn[i] <- output[[6]]
}

 save(parm_set,file = "output/bifurcationdata.RData")
```

```{r}
load("output/bifurcationdata.RData")
chaos <- function(value){
  if (value >= 3){
    return(3)
  } else{
    return(value)
  }
}
parm_set <- parm_set %>% 
  mutate(chaos_measure = sapply(periodicity_05, chaos))
  palette_11 <- brewer.pal(11, "Spectral") 
library(fields)

alpha_1 <- seq(round(Texas_best_parms$alpha_1,3)-0.3,
               round(Texas_best_parms$alpha_1,3)+0.3,0.005)
alpha_2 <- seq(round(Texas_best_parms$alpha_2,3)-0.1,
               round(Texas_best_parms$alpha_2,3)+0.1,0.002)
tau_2 <- seq(0.65,1.35,0.005)
plot_names <- c("Intensity","prop0_1")
legend_names <- c("Intensity","Under 1 Hospitalization Proportion")
file_names <- c("figures/fig3/C_i","figures/fig3/C_ii")
for (k in 1: length(plot_names)){
  plotname <- plot_names[k]
  # unpack into matrix
  mat <-matrix(ncol = length(tau_2), nrow = length(alpha_2))
  colnames(mat) <- tau_2
  rownames(mat) <- alpha_2
  for (j in 1:length(tau_2)){
    for (i in 1:length(alpha_2)){
      mat[i,j] <- parm_set[[plotname]][length(alpha_2)*(j-1)+i]
    }
  }
  png(paste0(file_names[k],'.png'),height =3.5, width = 4.5,units = "in", res =300)
  # pdf(paste0(file_names[k],'.pdf'),height =3.5, width = 4.5)
  par(mar = c(3.5, 3, 1, 1.5), mgp = c(1.6, 1.2, 0))
  image.plot(t(mat),
        xlab = 'Rel. Urban Contact Rate',
          ylab = 'Seasonal Forcing',
        col=coolwarm(20),
        legend.lab=legend_names[k],
        axes = F,
        legend.line = 2.5)
  axis(2,at=seq(0,1, length=length(alpha_2)), labels = round(alpha_2,2),tick = F,line = -0.7)
  axis(1,at=seq(0,1, length=length(tau_2)), labels = tau_2,tick = F,line = -0.7)
  dev.off()
}

alpha_1 <- seq(round(Texas_best_parms$alpha_1,3)-0.3,
               round(Texas_best_parms$alpha_1,3)+0.3,0.005)
alpha_2 <- seq(round(Texas_best_parms$alpha_2,4)-0.1,
               round(Texas_best_parms$alpha_2,4)+0.1,0.002)
tau_2 <- seq(0.65,1.35,0.005)
plot_names <- c("Intensity","prop0_1")
legend_names <- c("Intensity","Under 1 Hospitalization Proportion")
file_names <- c("figures/fig3/C_iii","figures/fig3/C_iv")
for (k in 1: length(plot_names)){
  plotname <- plot_names[k]
  # unpack into matrix
  mat <-matrix(ncol = length(tau_2), nrow = length(alpha_1))
  colnames(mat) <- tau_2
  rownames(mat) <- alpha_1
  for (j in 1:length(tau_2)){
    for (i in 1:length(alpha_1)){
      mat[i,j] <- parm_set[[plotname]][length(alpha_1)*(j-1)+i+length(alpha_2)*length(tau_2)]
    }
  }
  png(paste0(file_names[k],'.png'),height =3.5, width = 4.5,units = "in", res =300)
  par(mar = c(3.5, 3, 1, 1.5), mgp = c(1.6, 1.2, 0))
  image.plot(t(mat),
        xlab = 'Rel. Urban Contact Rate',
        ylab = 'Mean Transmission Rate',
        col=coolwarm(20),
        legend.lab=legend_names[k],
        axes = F,
        legend.line = 2.5)
  axis(2,at=seq(0,1, length=length(alpha_1)), labels = round(alpha_1,2),tick = F,line = -0.7)
  axis(1,at=seq(0,1, length=length(tau_2)), labels = tau_2,tick = F,line = -0.7)
  dev.off()
}

```

# example plots
```{r}
load("output/TX_parms.RData")

# Fix taus so there is no contact matrix amplification.
TX_parms[[4]]$tau_1 <- 0
TX_parms[[4]]$tau_2 <- 1

# Fix the vaccination rates to 0
TX_parms[[4]]$chi_m <- 0
TX_parms[[4]]$chi_b <- 0

# Make plots of the model and the Error bar plots of the prop of RSV across
# age categories.
param_set <- TX_parms[[4]]
param_set <- param_set[order(param_set$Loss, decreasing = FALSE),]
  parms <- as.list(param_set[1,]) # take only the best parameter set
  print(parms) 
for (i in 1:20){
  parms$alpha_2 <- parms$alpha_2-0.005
  # Get solution using best params
  solution <- ODE_solve_SIR(parms,States_IC_vec,20,522)
  
  # Get hospitalization data from solution
  hospitalizations <- Track_Hospitalizations(solution = solution,parms = parms)
  
  # Rescale timescales to start weeks at 0
  solution[,1] <- solution[,1]- min(solution[,1])
  hospitalizations[,1]<- hospitalizations[,1]-min(hospitalizations[,1])

  plot(hospitalizations[,1],rowSums(hospitalizations[,2:ncol(hospitalizations)]),col='black',lwd =2, type ='l', main = paste(parms$alpha_2))
}

```


```{r}
parms <- parm_set[parm_set$periodicity_025== 2,][1]
parms$tau_1 <- 0
parms$tau_2 <- 1
solution <- ODE_solve_SIR(parms,States_IC_vec,20,522)
  
  # Get hospitalization data from solution
  hospitalizations <- Track_Hospitalizations(solution = solution,parms = parms)
  
  # Rescale timescales to start weeks at 0
  solution[,1] <- solution[,1]- min(solution[,1])
  hospitalizations[,1]<- hospitalizations[,1]-min(hospitalizations[,1])

  plot(hospitalizations[,1],rowSums(hospitalizations[,2:ncol(hospitalizations)]),col='black',lwd =2, type ='l', main = paste(parms$alpha_2))
```

